1. Douglas A. Skoog, \textit{Principles of Instrumental Analysis}, 3rd Edition, Saunders, Philadelphia, 1984. Pagine 73-76.

2. Gary D. Christian and James E. O'Reilly, \textit{Instrumental Analysis}, Second Edition, Allyn and Bacon, Boston, 1986. Pagine 846-851.

3. Howard V. Malmstadt, Christie G. Enke, and Gary Horlick, \textit{Electronic Measurements for Scientists}, W. A. Benjamin, Menlo Park, 1974. Pagine 816-870.

4. Stephen C. Gates and Jordan Becker, \textit{Laboratory Automation using the IBM PC}, Prentice Hall, Englewood Cliffs, NJ, 1989.

5. Muhammad A. Sharaf, Deborah L Illman, and Bruce R. Kowalski, \textit{Chemometrics}, John Wiley and Sons, New York, 1986.

6. Peter Wentzell and Christopher Brown, Signal Processing in Analytical Chemistry, in \textit{Encyclopedia of Analytical Chemistry}, R.A. Meyers (Ed.), p. 9764\textendash{}9800, John Wiley \& Sons, Chichester, 2000 (\url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.124.2407&rep=rep1&type=pdf})

7. Constantinos E. Efstathiou, Educational Applets in Analytical Chemistry, Signal Processing, and Chemometrics. (\url{http://www.chem.uoa.gr/Applets/Applet_Index2.htm})

8. A. Felinger, Data Analysis and Signal Processing in Chromatography, Elsevier Science (19 May 1998).

9. Matthias Otto, Chemometrics: Statistics and Computer Application in Analytical Chemistry, Wiley-VCH (March 19, 1999). Some parts viewable in \href{http://books.google.com/books?q=Matthias+Otto&btnG=Search+Books}{Google Books}.

10. Steven W. Smith, \textit{The Scientist and Engineer's Guide to Digital Signal Processing.} (Downloadable chapter by chapter in PDF format from \url{http://www.dspguide.com/pdfbook.htm}). This is a much more general treatment of the topic. 

11. Robert de Levie, \href{http://www.amazon.com/Analytical-Chemistry-General-Scientific-Analysis/dp/0521644844}{\textit{How to use Excel in Analytical Chemistry and in General Scientific Data Analysis}}, Cambridge University Press; 1 edition (February 15, 2001), \textbf{ISBN-10:}0521644844. \href{http://www.google.com/url?sa=t&ct=res&cd=1&url=http\%3A\%2F\%2Fassets.cambridge.org\%2F97805216\%2F42828\%2Fsample\%2F9780521642828ws.pdf&ei=4Ul\_SKuZH5C48ASVzJzICw&usg=AFQjCNHe4iEMybvyCaXjp0EZy9S81S81HA&sig2=1qzXPv8WgZ9ktQH\_v-XeFg}{PDF excerpt}.

12. Scott Van Bramer, Statistics for Analytical Chemistry, \href{http://science.widener.edu/svb/stats/stats.html}{http://science.widener.edu/svb/stats/stats.htm}l.

13. Taechul Lee, \href{https://www.cheric.org/files/education/cyberlecture/e200113/e200113-101.pdf}{Numerical Analysis for Chemical Engineers}.

14. Educational Matlab GUIs, Georgia Institute of Technology. (\href{http://users.ece.gatech.edu/mcclella/matlabGUIs/}{http://spfirst.gatech.edu/matlab/})

15. Jan Allebach, Charles Bouman, and Michael Zoltowski, Digital Signal Processing Demonstrations in Matlab, Purdue University (\url{http://www.ecn.purdue.edu/VISE/ee438/demos/Demos.html})

16. Chao Yang, Zengyou He and Weichuan Yu, Comparison of public peak detection algorithms for MALDI mass spectrometry data analysis, \url{http://www.biomedcentral.com/1471-2105/10/4}

17. Michalis Vlachos, \href{http://alumni.cs.ucr.edu/~mvlachos/PKDD05/PKDD05\_Handout.pdf}{A practical Time-Series Tutorial with MATLAB}.

18. Laurent Duval, Leonardo T. Duarte, Christian Jutten, \href{https://pdfs.semanticscholar.org/presentation/a976/389cef473cd218a9ae3204419dfe60112efa.pdf}{\textit{An Overview of Signal Processing Issues in Chemical Sensing}}\textit{.}

19. Nicholas Laude, Christopher Atcherley, and Michael Heien, \textit{Rethinking Data Collection and Signal Processing. 1. Real-Time Oversampling Filter for Chemical Measurements,} \url{https://pubs.acs.org/doi/abs/10.1021/ac302169y}

20. P. E. S. Wormer, Matlab for Chemists, \url{http://www.math.ru.nl/dictaten/Matlab/matlab_diktaat.pdf}

21. Martin van Exter, Noise and Signal Processing, \href{http://www.physics.leidenuniv.nl/sections/cm/ip/Onderwijs/SVR/bestanden/noise-final.pdf}{http://molphys.leidenuniv.nl/\textasciitilde{}exter/SVR/noise.pdf}

22. Scott Sinex, Developer's Guide to Excelets, \url{http://academic.pgcc.edu/~ssinex/excelets/}

23. R. de Levie, Advanced Excel for scientific data analysis, Oxford University Press, New York (2004) 

24. S. K. Mitra, Digital Signal Processing, a computer-based approach, 4th ed, McGraw-Hill, New York, 2011.

25. ``Calibration in Continuum-Source AA by Curve Fitting the Transmission Profile'', T. C. O'Haver and J. Kindervater, \textit{J. of Analytical Atomic Spectroscopy} 1, 89 (\textbf{1986})

26. ``Estimation of Atomic Absorption Line Widths in Air-Acetylene Flames by Transmission Profile Modeling'', T. C. O'Haver and Jing-Chyi Chang, \textit{Spectrochim. Acta} 44B, 795-809 (\textbf{1989})

27. ``Effect of the Source/Absorber Width Ratio on the Signal-to-Noise Ratio of Dispersive Absorption Spectrometry'', T. C. O'Haver, \textit{Anal. Chem}. 68, 164-169 (\textbf{1991}).

28. ``Derivative Luminescence Spectrometry'', G. L. Green and T. C. O'Haver, \textit{Anal. Chem. 46}, 2191 (\textbf{1974}).

29. ``Derivative Spectroscopy'', T. C. O'Haver and G. L. Green, \textit{American Laboratory 7}, 15 (\textbf{1975}). 

30. ``Numerical Error Analysis of Derivative Spectroscopy for the Quantitative Analysis of Mixtures'', T. C. O'Haver and G. L. Green, \textit{Anal. Chem. 48}, 312 (\textbf{1976}).

31. ``Derivative Spectroscopy: Theoretical Aspects'', T. C. O'Haver, \textit{Anal. Proc. 19}, 22-28 (\textbf{1982}).

32. ``Derivative and Wavelength Modulation Spectrometry," T. C. O'Haver, \textit{Anal. Chem. 51}, 91A (\textbf{1979}).

33. ``A Microprocessor-based Signal Processing Module for Analytical Instrumentation'', T. C. O'Haver and A. Smith, \textit{American Lab. 13}, 43 (\textbf{1981}). 

34. ``Introduction to Signal Processing in Analytical Chemistry'', T. C. O'Haver, \textit{J. Chem. Educ}. 68 (\textbf{1991})

35. ``Applications of Computers and Computer Software in Teaching Analytical Chemistry'', T. C. O'Haver, \textit{Anal. Chem.} \textbf{68}, 521A (\textbf{1991}).

36. ``The Object is Productivity'', T. C. O'Haver, \textit{Intelligent Instruments and Computers} Mar-Apr, \textbf{1992}, p 67-70. 

37. Analysis software for spectroscopy and mass spectrometry, Spectrum Square Associates ( \url{http://www.spectrumsquare.com/}).

38. \textit{Fityk}, a program for data processing and nonlinear curve fitting. (\url{http://fityk.nieto.pl/})

39. Peak fitting in \textit{Origin} (\url{http://www.originlab.com/index.aspx?go=Products/Origin/DataAnalysis/PeakAnalysis/PeakFitting}) 

40. \textit{IGOR Pro 6}, software for signal processing and peak fitting (\url{http://www.wavemetrics.com/index.html})

41. \href{https://www.bioprocessonline.com/doc/software-for-automated-peak-separation-and-an-0001}{\textit{PeakFIT}, automated peak separation analysis}, Systat Software Inc..

42. \textit{OpenChrom}, open-source software for chromatography and mass spectrometry. (\url{http://www.openchrom.net/main/content/index.php})

43. W. M. Briggs, \textit{Do not smooth times series, you hockey puck!}, \url{http://wmbriggs.com/blog/?p=195}

44. Nate Silver, \textit{The Signal and the Noise}: \textit{Why So Many Predictions Fail-but Some Do not}, Penguin Press, 2012. ISBN 159420411X. A much broader look at "signal" and "noise", aimed at a general audience, but still worth reading.

45. David C. Stone, Dept. of Chemistry, U. of Toronto, \href{http://www.chem.utoronto.ca/coursenotes/analsci/stats/index.html}{Stats Tutorial - Instrumental Analysis and Calibration}.

46. Streamlining Digital Signal Processing: A Tricks of the Trade Guidebook, Richard G. Lyons, John Wiley \& Sons, 2012. 

47. Atomic spectra lines database. \url{http://physics.nist.gov/PhysRefData/ASD/} and \url{http://www.astm.org/Standards/C1301.htm}

48. Curve fitting to get overlapping peak areas (\href{http://matlab.cheme.cmu.edu/2012/06/22/curve-fitting-to-get-overlapping-peak-areas/\#13}{http://matlab.cheme.cmu.edu/2012/06/22/curve-fitting-to-get-overlapping-peak-areas})

49. Tony Owen, \href{http://www.chem.agilent.com/Library/primers/Public/59801397\_020660.pdf}{Fundamentals of Modern UV-Visible Spectroscopy}, Agilent Corp, 2000. 

50. Nicole K. Keppy, Michael Allen, Understanding Spectral Bandwidth and Resolution in the Regulated Laboratory, Thermo Fisher Scientific Technical Note: 51721. \url{http://www.analiticaweb.com.br/newsletter/02/AN51721_UV.pdf}

51. Martha K. Smith, "Common mistakes in using statistics", \url{http://www.ma.utexas.edu/users/mks/statmistakes/TOC.html}

52. Jan Verschelde, ``Signal Processing in MATLAB'', \url{http://homepages.math.uic.edu/~jan/mcs320s07/matlec7.pdf} 

53. H. Mark and J. Workman Jr, ``Derivatives in Spectroscopy'', Spectroscopy 18 (12). p.106.

54. Jake Blanchard, Comparing Matlab to Excel/VBA, \url{https://blanchard.ep.wisc.edu/PublicMatlab/Excel/Matlab_VBA.pdf}

55. Ivan Selesnick, "Least-squares with Examples in Signal Processing", \url{http://eeweb.poly.edu/iselesni/lecture_notes/least_squares/}

56. Tom O'Haver, "Is there Productive Life after Retirement?", \textit{Faculty Voice}, University of Maryland, April 24, 2014. \textbf{DOI:} 10.13140/2.1.1401.6005; URL: \href{http://imerrill.umd.edu/facultyvoice1/?p=3231}{https://terpconnect.umd.edu/\textasciitilde{}toh/spectrum/Retirement.pdf}

57. \url{http://www.dsprelated.com/}, the most popular independent internet resource for Digital Signal Processing (DSP) engineers around the world. 

58. John Denker, "Uncertainty as Applied to Measurements and Calculations", \url{http://www.av8n.com/physics/uncertainty.htm}\textcolor{color-8}{.} Excellent\textcolor{color-8}{.}

59. T. C. O'Haver, Teaching and Learning Chemometrics with Matlab, \textit{Chemometrics and Intelligent Laboratory Systems} 6, 95-103 (1989).

60. Allen B. Downey, "Think DSP", Green Tree Press, 2014. (\href{http://greenteapress.com/thinkdsp/thinkdsp.pdf}{153-page PDF download}). Python code instruction using sound as a basis.

61. Purnendu K. Dasgupta, et. al, "Black Box Linearization for Greater Linear Dynamic Range: The Effect of Power Transforms on the Representation of Data", \textit{Anal. Chem.} 2010, 82, 10143\textendash{}10150.

62. Joseph Dubrovkin, Mathematical Processing of Spectral Data in Analytical Chemistry: A Guide to Error Analysis, Cambridge Scholars Publishing, 2018 and 2019, 379 pages. ISBN 978-1-5275-1152-1. \href{http://www.cambridgescholars.com/mathematical-processing-of-spectral-data-in-analytical-chemistry}{Link}.

63. Power Law Approach as a Convenient Protocol for Improving Peak Shapes and Recovering Areas from Partially Resolved Peaks, M. Farooq Wahab, et. al., \textit{Chromatographia} (2018). \url{https://doi.org/10.1007/s10337-018-3607-0}. 

64. T. C. O’Haver, \textit{Interactive Computer Models for Analytical Chemistry Instruction}, \href{https://terpconnect.umd.edu/~toh/models/RegressionDemo.xls}{https://terpconnect.umd.edu/\textasciitilde{}toh/models}/, 1995.

65. T. C. O’Haver, \textit{Interactive Simulations of Basic Electronic and Operational Amplifier Circuits}, \url{https://terpconnect.umd.edu/~toh/ElectroSim}, (1996)

66. Signal Processing at Rice University. (\url{http://dsp.rice.edu/software/})

67. Steven Pinker, The Sense of Style: The Thinking Person's Guide to Writing in the 21st Century, New York, NY: Penguin, 2004.

68. Joseph Dubrovkin, \url{https://www.researchgate.net/profile/Joseph-Dubrovkin}

69. Separations at the Speed of Sensors, D. C. Patel, M. Farooq Wahab, T. C. O’Haver, and Daniel W. Armstrong, \textit{Analytical Chemist}ry \textbf{2018} 90 (5), 3349-3356, DOI: 10.1021/acs.analchem.7b04944

70. MF Wahab, TC O'Haver, F. Gritti, G. Hellinghausen, and DW Armstrong, ``Increasing chromatographic resolution of analytical signals using derivative enhancement approach,'' \textit{Talanta}, vol. 192, pp. 492\textendash{}499, \textbf{2019}

71. Yuri Kalambet, "Reconstruction of exponentially modified functions", \textbf{2019}. DOI: 10.13140/RG.2.2.12482.84160. \href{https://www.researchgate.net/publication/333237821\_Reconstruction\_of\_exponentially\_modified\_functions}{Link}. 

72. Yuri Kalambet, Yuri Kozmin, Andrey Samokhin, ``Comparison of integration rules in the case of very narrow chromatographic peaks'', \textit{Chemometrics and Intelligent Laboratory Systems} 179

May \textbf{2018}. DOI: 10.1016/j.chemolab.2018.06.001

73. Yuri Kalambet, et. al., "Reconstruction of chromatographic peaks using the exponentially modified Gaussian function", \textit{Journal of Chemometrics} June \textbf{2011}, 25(7):352 - 356. DOI: 10.1002/cem.1343\label{ref-0534}\label{ref-0535}\label{ref-0536}

74. Allen, L. C., Gladney, H. M., Glarum, S. H., J. Chem. Phys. 40, 3135 (\textbf{1964})

75. J. W. Ashley, Charles N. Reilley, "De-Tailing and Sharpening of Response Peaks in Gas Chromatography", \textit{Anal. Chem.}, 37, 6, 626-630, \textbf{1965}.

76. M. Johansson, M. Berglund and D. C. Baxter, ``Improving accuracy in the quantitation of overlapping, asymmetric, chromatographic peaks by deconvolution: theory and application to coupled gas chromatography atomic absorption spectrometry'', \textit{Spectrochemica Acta}, Vol 48B, p. 1393-1409, \textbf{1993}.

77. S. Sterlinski, "A Method for Resolution Enhancement of Interfering Peaks in Ge(Li) Gamma-Ray Spectra", \textit{J. of Radioanalytical Chemistry}, 31, 195-226, \textbf{1976}.

78. ``Importance of academic blogs'', Teachers Insurance and Annuity Association of America-College Retirement Equities Fund, New York, NY. \url{https://careerpurpose.com/industries/education/academic-blogs}.

79. Robi Polikar, The Wavelet Tutorial, \url{http://web.iitd.ac.in/~sumeet/WaveletTutorial.pdf}

80. C. Valens, ``A Really Friendly Guide to Wavelets'', \url{http://agl.cs.unm.edu/~williams/cs530/arfgtw.pdf}

81. Brani Vidakovic and Peter Mueller, ``Wavelets for Kids'',\url{http://www.gtwavelet.bme.gatech.edu/wp/kidsA.pdf} 

82. Amara Graps, ``An Introduction to Wavelets'' \url{https://www.eecis.udel.edu/~amer/CISC651/IEEEwavelet.pdf}

83. Muhammad Ryan, ``What is Wavelet and How We Use It for Data Science'', \url{https://towardsdatascience.com/what-is-wavelet-and-how-we-use-it-for-data-science-d19427699cef}

84. \textcolor{color-23}{Michael X.} \textcolor{color-23}{Cohen}, ``A better way to define and describe Morlet wavelets for time-frequency analysis'', \textit{NeuroImage}, Volume 199, 1 October \textbf{2019}, Pages 81-86. 

85. Wahab M. F, O’Haver T. C., ``Wavelet transforms in separation science for denoising and peak overlap detection.'' \textit{J Sep Sci}. 43 (9-10) 1615\textendash{}2012 (\textbf{2020}). ISSN 1615-9306; \url{https://doi.org/10.1002/jssc.202000013}

86. G. K. Wertheim, \textit{J. of Electron Spectroscopy and Related Phenomena}, 6 (\textbf{1975}) 239-251.

87. R. E. Sturgeon, et. al., Atomization in graphite-furnace atomic absorption spectrometry. Peak-height method vs. integration method of measuring absorbance. \textit{Anal. Chem}. 47, 8, 1240\textendash{}1249 (1075) \url{https://doi.org/10.1021/ac60358a039}

88. Sunaina et al, ``Calculating numerical derivatives using Fourier transform: some pitfalls and how to avoid them'', \textit{Eur. J. Phys.} 39, 065806, \textbf{2018}

89. Sinex, Scott A, Investigating types of errors. \textit{Spreadsheets in Education} 2.1 (\textbf{2005}): 115-124.

90. Catherine Perrin, Beata Walczak, and D\'{e}sir\'{e} Luc Massart, ``Quantitative Determination of the Components in Overlapping Chromatographic Peaks Using Wavelet Transform'', \textit{Analytical Chemistry} \textbf{2001} 73 (20), 4903-4917

DOI: 10.1021/ac010416a

91. F. Gritti, S. Besner, S. Cormier, M. Gilar, Applications of high-resolution recycling liquid chromatography: from small to large molecules, \textit{Journal of Chromatography} A 1524 (2017) 108-120.

92. 90. Desimoni E. and Brunetti B., "About Estimating the Limit of Detection by the Signal to Noise Approach", \textit{Pharmaceutica Analytica Acta} 67, 4, \textbf{2015}. DOI: 10.4172/2153-2435.100035. \href{https://www.longdom.org/open-access/about-estimating-the-limit-of-detection-by-the-signal-to-noise-approach-2153-2435-1000355.pdf}{PDF link}.

93. Royal Society of Chemistry Analytical Methods Committee, ``Recommendations for the Definition, Estimation and Use of the Detection Limit'', \textit{Analyst}, Feb. \textbf{1987}, vol.112, p. 199.


\ifLangEnglish
	\chapter{Publications that cite the use of my book, programs and/or documentation\label{ref-0538}}

	Last updated January 2021

	If you have published a paper using these programs that you would like me to include here, please email the paper, or a citation to it, to Tom O'Haver at toh@umd.edu
\else
	\chapter{Pubblicazioni che citano questo libro, i programmi e/o la documentazione\label{ref-0537}}

	Ultimo aggiornamento Gennaio 2021

	Se \`{e} stato pubblicato un articolo utilizzando questi programmi che si vorrebbe includere in questa lista, si pregha di inviare il documento, o una citazione, a Tom O'Haver a toh@umd.edu
\fi


1. Poppi, R. J., Vazquez, P. A., \& Pasquini, C. (\textbf{1992}). Fast scanning Hadamard spectrophotometer. \textit{Applied Spectroscopy}, 46(12), 1822-1827.

2. Ghatee, M. H., and A. Boushehri. "Modulation of the integrated rate equation of a composite system for the kinetic parameters." \textit{Chemometrics and intelligent laboratory} systems 25.1 (\textbf{1994}): 43-49.

3. C.W.K. Chow, D.E. Davey, Dennis Mulcahy, T.C.W. Yeow, Signal enhancement of potentiometric stripping analysis using digital signal processing, \textit{Analytica Chimica} Acta 307(1):15-26, April \textbf{1995}

DOI: 10.1016/0003-2670(95)00023-S

4. Ringe, Steven A. "Hydrogen-extended defect interactions in heteroepitaxial InP materials and devices." \textit{Solid-State Electronics} 41.3 (\textbf{1997}): 359-380.

5. Chow, Christopher WK, David Edward Davey, and D. E. Mulcahy. "Signal filtering of potentiometric stripping analysis using Fourier techniques." \textit{Analytica chimica acta} 338.3 (\textbf{1997}): 167-178.

6. Leung, Alexander Kai-man, Foo-Tim Chau, and Jun-bin Gao. "Wavelet transform: a method for derivative calculation in analytical chemistry." \textit{Analytical} Chemistry 70.24 (\textbf{1998}): 5222-5229.

7. Harris, D. C. (\textbf{1998}). ``Spektralphotometer''. In \textit{Lehrbuch der Quantitativen Analyse} (pp. 695-746). Vieweg+ Teubner Verlag. Link.

8. Keyhani, Ali, Wenzhe Lu, and Gerald T. Heydt. "Neural network based composite load models for power system stability analysis." IEEE International Conference on Computational Intelligence for Measurement Systems and Applications. \textbf{2005}.

9. Fern\'{a}ndez, Mario, and J. Ricardo P\'{e}rez-Correa. "Instrumentation for Monitoring SSF Bioreactors." Solid-State Fermentation Bioreactors. Springer Berlin Heidelberg, \textbf{2006}. 363-374

10. Richard Graham, Ring Laser Gain Media, Thesis, \url{http://ir.canterbury.ac.nz/bitstream/10092/1377/1/thesis_fulltext.} pdf (\textbf{2006})

11. Sheaff, Chrystal N., Delyle Eastwood, and Chien M. Wai. "Increasing selectivity for TNT-based explosive detection by synchronous luminescence and derivative spectroscopy with quantum yields of selected aromatic amines." \textit{Applied spectroscopy} 61.1 (\textbf{2007}): 68-73.

12. Hovick, James W., Michael Murphy, and J. C. Poler. "" Audibilization" in the chemistry

laboratory: An introduction to correlation techniques for data extraction." \textit{J. Chem. Educ} 84.8 (\textbf{2007}): 1331.

13. de Arag\~{a}o, Bernardo Jos\'{e} Guilherme, and Younes Messaddeq. "PEAK SEPARATION IN SPECTRAL ANALYSIS." (\textbf{2007}). Link.

14. Ingersoll, Justin Edward. A Regularization Technique for the Analysis of Photographic Data Used in Chemical Release Wind Measurements. ProQuest, \textbf{2008}.

15. Dinesh, S. "The Effect of Smoothing on the Extraction of Drainage Networks from Simulated Digital Elevation Models." \textit{Journal of Applied Sciences Research} 4.11 (\textbf{2008}): 1356-1360.

16. Jed A. Meltzer, Hitten P. Zaveri, Irina I. Goncharova, Marcello M. Distasio, Xenophon Papademetris, Susan S. Spencer, Dennis D. Spencer and R. Todd Constable, ''Effects of Working Memory Load on Oscillatory Power in Human Intracranial EEG'', \textit{Cereb. Cortex} (\textbf{2008}) 18 (8): 1843-1855. doi: 10.1093/cercor/bhm213

17. Sheaff, Chrystal N., et al. "Fluorescence detection and identification of tagging agents and impurities found in explosives." \textit{Applied spectroscopy} 62.7 (\textbf{2008}): 739-746.

18. "A regularization technique for the analysis of photographic data used in chemical release wind measurements", JE Ingersoll, \textbf{2008}, books.google.com

19. "An application of detection function for the eye blinking detection", Pander, T. Przybyla, T.; Czabanski, Human System Interactions \textbf{2008} Conference: 25-27 May 2008, Page(s): 287- 291

20. "Isotopically labeled oxygen studies of the NOx exchange behavior of La2CuO4 to determine potentiometric sensor response mechanism" F.M. Van Assche IV, E.D. Wachsman, \textit{Solid State Ionics,} Volume 179, Issue 39, 15 December \textbf{2008}, Pages 2225\textendash{}2233

21. "High-speed laryngoscopic evaluation of the effect of laryngeal parameter variation on aryepiglottic trilling." Moisik, Scott R., John H. Esling, and Lise CrevierBuchman. poster, \url{http://www.ncl.ac.uk/linguistics/assets/documents/} MoisikEslingBuchman\_NewcastleP haryngealsPoster\_2009. Pdf (\textbf{2009}).

22. Tricas, Marazico, and Juan Ignacio. "Auto configuration dans LTE: proc\'{e}d\'{e}s de mesure de l’occupation du canal radio pour une utilisation optimis\'{e}e du spectre.", "Auto configuration in LTE: measuring the occupancy of the radio channel for optimized use of the spectrum" (\textbf{2009}). PDF link.

23."Early age concrete strength monitoring with piezoelectric transducers by the harmonic frequencies method", Thomas J. Kelleher, \textbf{2009}.\url{http://www.engin.swarthmore.edu/e90/2008/reports/Thomas\%20Kelleher.pdf}

24. "Information management for high content live cell imaging", Daniel Jameson, David A Turner, John Ankers, Stephnie Kennedy, Sheila Ryan, Neil Swainston, Tony Griffiths, David G Spiller, Stephen G Oliver, Michael RH White, Douglas B Kell and Norman W Paton, \textit{BMC Bioinformatics} \textbf{2009}, 10:226 doi:10.1186/1471-2105-10-2263

25. "Human-Computer Systems Interaction: Backgrounds and Applications", edited by Zdzislaw S. Hippe, Juliusz Lech Kulikowski, Springer (Sep 30, \textbf{2009}), page 191.

26. "Multiplexed DNA detection using spectrally encoded porous SiO2 photonic crystal particles", SO Meade, MY Chen, MJ Sailor, \textit{Anal. Chem}., \textbf{2009}, 81 (7), pp 2618\textendash{}2625. DOI: 10.1021/ac802538x

27. "Prolonged stimulus exposure reveals prolonged neurobehavioral response patterns, Brett A. Johnson, Cynthia C. Woo, Yu Zeng, Zhe Xu, Edna E. Hingco, Joan Ong, Michael Leon. \textit{The Journal of Comparative Neurology}, Volume 518, Issue 10, pages 1617\textendash{}1629, 15 May \textbf{2010}

28."Alternative Measures of Phonation: Collision Threshold Pressure and Electroglottographic Spectral Tilt: Extra: Perception of Swedish Accents." Enflo, Laura. (\textbf{2010}). Full Text.

29. Botcharova, Maria. "Changes in structure of EEG-EMG coherence during brain development: analysis of experimental data and modeling of putative mechanisms." (\textbf{2010}) [PDF] from ucl.ac.uk

30."Vowel Dependence for Electroglottography and Audio Spectral Tilt", L Enflo, Proceedings of Fonetik, \textbf{2010}. Full text.

31. "Rapid and accurate detection of plant miRNAs by liquid northern hybridization.", Wang, Xiaosu, Yongao Tong, and Shenghua Wang. International journal of molecular sciences 11.9 (\textbf{2010}): 3138-3148.

32. Nusz, G. J. (\textbf{2010}). Label-free biodetection with individual plasmonic nanoparticles (Doctoral dissertation, Duke University).

33. Khudaish, Emad A., and Aysha A. Al Farsi. "Electrochemical oxidation of dopamine and ascorbic acid at a palladium electrode modified with in situ fabricated iodine-adlayer in alkaline solution." Talanta 80.5 (\textbf{2010}): 1919-1925.

34. "Advances in Music Information Retrieval", edited by Zbigniew W. Ras, Alicja Wieczorkowska, Springer, \textbf{2010}, page 135.

35. Bilal, M., Sharif, M., Jaffar, M. A., Hussain, A., \& Mirza, A. M. (2010, May). Image restoration using modified hopfield fuzzy regularization method. In Future Information Technology (FutureTech), \textbf{2010} 5th International Conference on (pp. 1-6). IEEE.

36. Rim, Jung Ho. "Preparation and Characterization of Sources for Ultra-high Resolution Microcalorimeter Alpha Spectrometry." The Pennsylvania State University (\textbf{2010}). PDF link.

37. Xiaosu Wang, Yongao Tong and Shenghua Wang, Rapid and Accurate Detection of Plant miRNAs by Liquid Northern Hybridization, Int. J. Mol. Sci. \textbf{2010}, 11(9), 3138-3148; doi:10.3390/ijms11093138

38. ``Radio Frequency Fuel Gauging with Neuro-Fuzzy Inference Engine For Future Spacecrafts''. Kumagai, A., Liu, T. I., \& Sul, D. In Proceedings of the 10th IASTED, International Conference, \textbf{2010} (Vol. 674, No. 020, p. 243).

39. "Automatic Seizure Detection in ECoG by Differential Operator and Windowed Variance," Majumdar, K.K.; Vardhan, P., Neural Systems and Rehabilitation Engineering, IEEE Transactions on, vol.19, no.4, pp.356,365, Aug. \textbf{2011}

40. "Genetic algorithm with peaks adaptive objective function used to fit the EPR powder spectrum", Sebastian Grzegorz \.{Z}urek, Applied Soft Computing, Volume 11, Issue 1, January \textbf{2011}, Pages 1000\textendash{}1007

41. "Determination of sea conditions for wave energy conversion by spectral analysis", B Yagci, P Wegener, EEE Transactions on Power Delivery, 18(2): 372\textendash{}376, \textbf{2011}.

42. "Push-broom hyperspectral imaging for elemental mapping with glow discharge optical emission spectrometry", G Gamez, D Frey, J Michler - J. Anal. At. Spectrom., \textbf{2011}, 65, 85\textendash{}98

43."Dual-order snapshot spectral imaging of plasmonic nanoparticles", Gregory J. Nusz, Stella M. Marinakos, Srinath Rangarajan, and Ashutosh Chilkoti, Applied Optics, Vol. 50, Issue 21, pp. 4198-4206 (\textbf{2011}) \url{http://dx.doi.org/10.1364/AO.50.004198}

44. Sugandharaju, Ravi Kumar Chatnahalli. ``Gaussian Deconvolution and MapReduce Approach for Chipseq Analysis''. Dissertation. University of Cincinnati, \textbf{2011}.

45. "Parallel Deconvolution Algorithm in Perfusion Imaging" F Zhu, DR Gonzalez, T Carpenter, Healthcare Informatics, Imaging and Systems Biology (HISB), 2011 First IEEE International Conference, 26-29 July \textbf{2011}

46. "Field observations of infragravity waves and their behaviour on rock shore platforms" Edward P. Beetham, Paul S. Kench, Earth Surface Processes and Landforms, Volume 36, Issue 14, pages 1872\textendash{}1888, November \textbf{2011}

47. "Majority Voting: Material Classification by Tactile Sensing Using Surface Texture", Jamali, N., Sammut, C., IEEE Transactions on Robotics, Volume: 27, Issue: 3, Page(s): 508 - 521, June \textbf{2011}

48. Yuan, Yuan, Yishan Luo, and Albert Chung. "VE-LLI-VO: Vessel enhancement using local line integrals and variational optimization." IEEE Transactions on Image Processing 20.7 (\textbf{2011}): 1912-1924.

49. ''Demand Estimation with Automated Meter Reading in a Distribution Network'', Aksela, K. and Aksela, M., J. Water Resour. Plann. Manage., 137(5), 456\textendash{}467 (\textbf{2011}). doi: 10.1061/(ASCE) WR.1943-5452.0000131

50. Ochoa, Jeimy Catherine Mill\'{a}n. Design and Development of a Localization System for a Sensor Network in Collective Symbiotic Organisms. Diss. Universit\"{a}tsbibliothek der Universit\"{a}t Stuttgart, \textbf{2011}.

51. "Genetic algorithm with peaks adaptive objective function used to fit the EPR powder spectrum", Sebastian Grzegorz \.{Z}urek, Journal Applied Soft Computing archive. Volume 11, Issue 1, January \textbf{2011}, pages 1000-1007

52. Hornung, J. P. (\textbf{2011}). Exploring the potential for using deep-sea bamboo corals (Isidella sp.) for paleoceanographic reconstructions (Doctoral dissertation).

53. Boll, Marie-Theres. Ein neues Konzept zur automatisierten Bewertung von Fertigkeiten in der minimal invasiven Chirurgie f\"{u}r Virtual-Reality-Simulatoren in GridUmgebungen. Vol. 38. KIT Scientific Publishing, \textbf{2011}. Link.

54. "Development of ECG signal interpretation software on Android 2.2, Hermawan, K.; Iskandar, A.A.; Hartono, R.N., "Instrumentation, Communications, Information Technology, and Biomedical Engineering (ICICI-BME), 2011 2nd International Conference, vol., no., pp.259,264, 8-9 Nov. \textbf{2011}

doi: 10.1109/ICICI-BME.2011.6108621

55. Choi, Sheng Heng. "Signal processing and amplifier design for inexpensive genetic analysis instruments." (\textbf{2011}). \url{https://era.library.ualberta.ca/files/qr46r139p\#.WifTkEqnGUk}

56. Hoffman, Galen Brandt. Direct Write of Chalcogenide Glass Integrated Optics Using Electron Beams. Diss. The Ohio State University, \textbf{2011}. Direct link.

57. Bai, Er-Wei, et al. "Detection of radionuclides from weak and poorly resolved spectra using Lasso and subsampling techniques." Radiation Measurements 46.10 (\textbf{2011}): 1138-1146.

58. Sugandharaju, Ravi Kumar Chatnahalli. Gaussian Deconvolution and MapReduce Approach for Chipseq Analysis. Diss. University of Cincinnati, \textbf{2011}.

59.``Automated peak alignment for nucleic acid capillary electrophoresis data by dynamic programming''. Fethullah Karabiber, Kevin Weeks, and Oleg V. Favorov. In Proceedings of the 2nd ACM Conference on Bioinformatics, Computational Biology and Biomedicine (BCB '11). ACM, New York, NY, USA, \textbf{2011}. pages 544-546. DOI=10.1145/2147805.2147895 \url{http://doi.acm.org/10.1145/2147805.2147895}

60.Shin, Sung-Hwan, et al. "Mass estimation of impacting objects against a structure using an artificial neural network without consideration of background noise." Nuclear Engineering and Technology 43.4 (\textbf{2011}): 343-354.

61. Taibo, Mar\'{i}a Luisa G\'{o}mez, et al. "Matching needs and capabilities with assistive technology in an amyotrophic lateral sclerosis patient." Accessibility, Inclusion and Rehabilitation using Information Technologies (\textbf{2011}): 21.

62. Paul, Ruma R., Victor C. Valgenti, and Min Sik Kim. "Real-time Netshuffle: Graph distortion for on-line anonymization." Network Protocols (ICNP), 2011 19th IEEE International Conference on. IEEE, \textbf{2011}.

63. Lopez-Castellanos, V. (\textbf{2011}). Ultrawideband time domain radar for time reversal applications (Doctoral dissertation, The Ohio State University).

64. "Electricity gain via integrated operation of turbine generator and cooling tower using local model network." Pan, Tian-Hong, et al. Energy Conversion, IEEE Transactions on 26.1 (\textbf{2011}): \textbf{245}-255.

65. "Dynamic analysis of electronic devices' power signatures, Marcu, M.; Cernazanu, C., " Instrumentation and Measurement Technology Conference (I2MTC), \textbf{2012} IEEE International, vol., no., pp.117,122, 13-16 May \textbf{2012.} doi: 10.1109/I2MTC.2012.6229562

66. "Experimental comparison among pileup recovery algorithms for digital gamma ray spectroscopy" El-Tokhy, M.S. Mahmoud, I.I. ; Konber, H.A. Informatics and Systems (INFOS), 2012 8th International Conference on 14-16, May \textbf{2012}

67. Kwon, Soonil. "Voice-driven sound effect manipulation." International Journal of Human-Computer Interaction 28.6 (\textbf{2012}): 373-382.

68. "Distributed representation of chemical features and tunotopic organization of glomeruli in the mouse olfactory bulb" Limei Maa, Qiang Qiua, Stephen Gradwohla, Aaron Scotta, Elden Q. Yua, Richard Alexandera, Winfried Wiegraebea, and C. Ron Yu, Proceeding of the National Academy of Sciences, April 3, \textbf{2012} vol. 109, no. 14, pages 5481-5486.

69. Hofler, Alicia S. Optimization Framework for a Radio Frequency Gun Based\textbackslash  Injector. Old Dominion University, PhD dissertation, \textbf{2012}.

70. "A Robust Heart Sound Segmentation and Classification Algorithm using Wavelet Decomposition and Spectrogram." Deng, Yiqi, and Peter J. Bentley. \textbf{2012}. Full text:

\url{http://www.peterjbentley.com/heartworkshop/challengepaper3.pdf}

71.``Detecting STR peaks in degraded DNA samples''. Marasco, E., Ross, A., Dawson, J., Moroose, T., \& Ambrose, T.Proc. of 4th International Conference on Bioinformatics and Computational Biology (BICoB), (Las Vegas, USA), March \textbf{2012}. Full text: \url{http://www.cse.msu.edu/~rossarun/pubs/RossDNAEnhanement_BICoB2011.pdf}

72. "Saccades detection in optokinetic nystagmus-a fuzzy approach." PANDER, Tomasz, et al. , Journal of Medical Informatics \& Technologies 19 (\textbf{2012}): 33-39.

73. "Grain-size properties and organic-carbon stock of Yedoma Ice Complex permafrost from the Kolyma lowland, northeastern Siberia", J Strauss, L Schirrmeister, S Wetterich, Andreas Borchers, Sergei P. Davydov, Global Biogeochemical Cycles, Volume 12, \textbf{2012}.

74."An Early Prediction of Cardiac Risk using Augmentation Index Developed based on a

Comparative Study." Manimegalai, P., Delpha Jacob, and K. Thanushkodi. ,

International Journal of Computer Applications 50 (2012). Abstract.

75. ``Determina\c{c}\~{a}o Da Estabilidade Oxidativa De Biocombust\'{i}veis,'' Bruno A. F. Vitorino, Franz H. Neff, Elmar U. K. Melcher, Antonio M. N. Lima, Anais do XIX Congresso Brasileiro de Autom\'{a}tica, CBA 2012.

\url{http://www.eletrica.ufpr.br/anais/cba/2012/Artigos/100018.pdf}

76."Efficacy of Differential Operators in Brain Electrophysiological Signal Processing: A Case Study in Epilepsy."Majumdar, Kaushik, and Pratap Vardhan. 2012 Full text.

77. Snider, W. (\textbf{2012}). Electro-optically Tunable Microring Resonators for Non-Linear Frequency Modulated Waveform Generation (Doctoral dissertation, Texas A \& M University).

78."9.0 Experimental\textendash{}Two-Dimensional GCxGC." Technologies towards the Development of a Lab-on-a-Chip GCxGC for Environmental Research (\textbf{2012}). Full text. A Thesis by Jaydene Halliday, BSc MRSC

79. "BaNa: A hybrid approach for noise resilient pitch detection," He Ba; Na Yang; Demirkol, I.; Heinzelman, W., Statistical Signal Processing Workshop (SSP), \textbf{2012} IEEE, vol., no., pp.369,372, 5-8 Aug. 2012. doi: 10.1109/SSP.2012.6319706

80. Tripathi, Ashish. THE NEW IMAGE PROCESSING ALGORITHM FOR\textbackslash  QUALITATIVE AND QUANTITATIVE STM DATA ANALYSIS. Diss. \textbf{2012}.

81. Skelton, Martin. "Diffusion of Innovation System Elements-A Novel Method to Study Technology Development and Its Application to Wind Power." (\textbf{2012}). [PDF] from chalmers.se

82. Pander, T., et al. "A new method of saccadic eye movement detection for optokinetic nystagmus analysis." Engineering in Medicine and Biology Society (EMBC), \textbf{2012} Annual International Conference of the IEEE. IEEE, \textbf{2012}.

83. Mahmoud, I. I., M. S. El\_Tokhy, and H. A. Konber. "Pileup recovery algorithms for digital gamma ray spectroscopy." Journal of Instrumentation 7.09 (\textbf{2012}): P09013.

84. Zhu, Fan, et al. "Parallel perfusion imaging processing using GPGPU." Computer methods and programs in biomedicine 108.3 (\textbf{2012}): 1012-1021.

85. Cuss, C. W., and Celine Gu\'{e}guen. "Determination of relative molecular weights of fluorescent components in dissolved organic matter using asymmetrical flow fieldflow fractionation and parallel factor analysis." Analytica chimica acta 733 (\textbf{2012}): 98- 102.

86. Olugboji, Oluwafemi A., and Jack M. Hale. "Development of Damage Reconstruction Techniques from Impulsive Events Based on Measurements Made Remotely." ASME 2012 International Mechanical Engineering Congress and Exposition. American Society of Mechanical Engineers, \textbf{2012}.

87. Dickson, B., and M. Craig. "Deconvolving gamma-ray logs by adaptive zone refinement." Geophysics 77.4 (\textbf{2012}): D159-D169.

88. ``SmartBells: RFID-Enhanced System to Monitor Free Weight Exercises. "Chaudhri, Rohit, and Gaetano Borriello. \textbf{2012} Full text.

89. "Diffusion of Innovation System Elements-A Novel Method to Study Technology Development and Its Application to Wind Power." Skelton, Martin. (\textbf{2012}). Fulltext.

90. Grotenhuis, Michael Gary. "An Overview of the Maximum Entropy Method of Image Deconvolution." A University of Minnesota\textendash{}Twin Cities ``Plan B'' Master’s paper, \textbf{2012}.

91. "On comet attitude determination of Rosetta lander Philae through nonlinear optimal system identification." Caputo, Gianluca. (\textbf{2012}). Full text.

92. Valadares$^{1}$, D. C., Vitorino, B. A., Neta, M. L. N., Batista, E. S., Santos, M. V., Neff, F. H., \& Melcher, E. N. (\textbf{2012}). System for Analysis of the Biodiesel Quality.

93. Mukhopadhyay, C. K., et al. "Acoustic emission during fracture toughness tests of SA333 Gr. 6 steel." Engineering Fracture Mechanics 96 (\textbf{2012}): 294-306.

94. Huang, Zifang. "Knowledge-Assisted Sequential Pattern Analysis: An Application in Labor Contraction Prediction." (\textbf{2012}). PDF link.

95. van de Voort, Frederik R., and David Pinchuk. "System and Method for Determining Base Content of a Hydrophobic Fluid." U.S. Patent Application 13/171,566.

96. Hoerndli, Fr\'{e}d\'{e}ric J., et al. "Kinesin-1 regulates synaptic strength by mediating the delivery, removal, and redistribution of AMPA receptors." Neuron 80.6 (\textbf{2013}): 1421-1437.

97. Brockie, Penelope J., et al. "Cornichons control ER export of AMPA receptors to regulate synaptic excitability." Neuron 80.1 (\textbf{2013}): 129-142.

98. \v{Z}\'{a}\v{c}ik, Michal. \v{S}umov\'{a} spektroskopie pro biologii. Diss. Vysok\'{e} u\v{c}en\'{i} technick\'{e} v Brn\v{e}. Fakulta elektrotechniky a komunika\v{c}n\'{i}ch technologi\'{i}, \textbf{2013}.

99. Phillips, James William, and Yi Jin. "Systems and methods for modulating the electrical activity of a brain using neuro-EEG synchronization therapy." U.S. Patent No. 8,465,408. 18 Jun. \textbf{2013}.

100. Moon, Jim, et al. "Body-worn vital sign monitor." U.S. Patent No. 8,364,250. 29 Jan. \textbf{2013}.

101. Hao, Manzhao, et al. "Corticomuscular Transmission of Tremor Signals by Propriospinal Neurons in Parkinson's Disease." PloS one 8.11 (\textbf{2013}): e79829.

102. McCOMBIE, Devin, Marshal Dhillon, and Matt Banet. "Method for measuring patient motion, activity level, and posture along with PTT-based blood pressure." U.S. Patent No. 8,475,370. 2 Jul. 2013.

103. Banet, Matt, Devin McCombie, and Marshal Dhillon. "Body-worn monitor for measuring respiration rate." U.S. Patent No. 8,545,417. 1 Oct. \textbf{2013}.

104. Banet, Matt, and Jim Moon. "Body-worn vital sign monitor." U.S. Patent No. 8,591,411. 26 Nov. \textbf{2013}.

105. Mccombie, Devin, et al. "Alarm system that processes both motion and vital signs using specific heuristic rules and thresholds." U.S. Patent No. 8,594,776. 26 Nov. \textbf{2013}.

106. Banet, Matt, Marshal Dhillon, and Devin McCombie. "Body-worn system for measuring continuous non-invasive blood pressure (cNIBP)." U.S. Patent No. 8,602,997. 10 Dec. \textbf{2013}.

107. Moon, Jim, et al. "Body-worn pulse oximeter." U.S. Patent No. 8,437,824. 7 May \textbf{2013}.

108. Cheng, Chunmei, et al. "Remote sensing estimation of Chlorophyll and suspended sediment concentration in turbid water based on spectral separation." Optik-International Journal for Light and Electron Optics 124.24 (\textbf{2013}): 6815-6819.

109. Phillips, James William, and Yi Jin. "Systems and methods for neuro-EEG synchronization therapy." U.S. Patent No. 8,585,568. 19 Nov. \textbf{2013}.

110. Khvostichenko, Daria S., et al. "An X-ray transparent microfluidic platform for screening of the phase behavior of lipidic mesophases." Analyst 138.18 (\textbf{2013}): 5384- 5395.

111. ``A signal alignment method based on DTW with new modification'', Karabiber, F.; Bilgisayar Muhendisligi Bolumu; Balcilar, M. Signal Processing and Communications Applications Conference (SIU), \textbf{2013} 21st, 24-26 April 2013. ISBN: 978-1-4673-5562-9; DOI: 10.1109/SIU.2013.6531176

112. ``An automated signal alignment algorithm based on dynamic time warping for capillary electrophoresis data'', Turkish Journal of Electrical Engineering \& Computer Sciences, Fethullah KARAB\.{I}BER, 21, (\textbf{2013}), 851-863. Full text: pdf

113. "Traditional Asymmetric Rhythms: A Refined Model of Meter Induction Based On Asymmetric Meter Templates'', Fouloulis, Thanos, Aggelos Pikrakis, and Emilios Cambouropoulos, Proceedings of the Third International Workshop on Folk Music Analysis (FMA2013). \textbf{2013}. ISBN 978-90-70389-78-9

114. "Comparison of two methods for measuring ${\upgamma}$-H2AX nuclear fluorescence as a marker of DNA damage in cultured human cells: applications for microbeam radiation therapy." Anderson, D., et al. , Journal of Instrumentation 8.06 (\textbf{2013}): C06008. Full text PDF.

115. Ayodeji, Olugboji Oluwafemi, Jonathan Yisa Jiya, and Jack M. Hale. "Event Reconstruction by Digital Filtering." Advances in Signal Processing 1.3 (\textbf{2013}): 48-56.

116. ``A conserved aromatic residue regulating photosensitivity in short-wavelength sensitive cone visual pigments''. Kuemmel, C. M., Sandberg, M. N., Birge, R. R., \& Knox, B. E. Biochemistry, 52(30), 5084-5091 (\textbf{2013}).

117. ``Measurement of The Lightweight Rotor Eigenfrequencies And Tuning Of Its\textbackslash  Model Parameters,'' Lubo\v{s} SMOL\'{l}K, Michal HAJ\v{Z}MAN, Transactions of the V\v{S}B \textendash{} Technical University of Ostrava, Mechanical Series, No. 1, \textbf{2013}, vol. LIX. FullEnglish text.

118. "Investigation of the phase separation of PNIPAM using infrared spectroscopy together with multivariate data analysis." Munk, Tommy, et al. , Polymer 54.26 (\textbf{2013}): 6947-6953. Abstract.

119. ``Phase separation in InxGa1 xN (0.10{\textless} x{\textless} 0.40).'' Belyaev, K. G., Rakhlin, M. -V., Jmerik, V. N., Mizerov, A. M., Kuznetsova, Y. V., Zamoryanskaya, M. V., ... \& Toropov, A. A. (2013). Physica Status Solidi (c), 10 (3), 527-531.

120. "Corticomuscular Transmission of Tremor Signals by Propriospinal Neurons in Parkinson's Disease." Hao, Manzhao, et al. , PloS one 8.11 (\textbf{2013}): e79829.

121. "Sickle-shaped voxel approach to enhance automatic reclaiming operation using bucket wheel reclaimer," Maung Thi Rein Myo; Tien-Fu Lu, Industrial Electronics and Applications (ICIEA), 2013 8th IEEE Conference on, vol., no., pp.1700,1705, 19- 21 June \textbf{2013}. doi: 10.1109/ICIEA.2013.6566642

122. "Review of software tools for design and analysis of large-scale MRM proteomic datasets." Colangelo, Christopher M., et al., Methods 61.3 (\textbf{2013}): 287-298.

123. Carabetta, Valerie J., et al. "A complex of YlbF, YmcA and YaaT regulates sporulation, competence and biofilm formation by accelerating the phosphorylation of Spo0A." Molecular microbiology 88.2 (\textbf{2013}): 283-300.

124. Web, N. L. P. M. L., and Andrew Rosenberg. "Ensemble Methods." (\textbf{2013}).

125. Cannon, Robert William, ``Automated Spectral Identification of Materials using Spectral Identity Mapping'', \textbf{2013}, Master of Science in Chemistry, Cleveland State University, College of Sciences and Health Professions.

126. MS Freeman, ZI Cleveland, Y Qi, Enabling hyperpolarized 129Xe MR spectroscopy and imaging of pulmonary gas transfer to the red blood cells in transgenic mice expressing human hemoglobin'', Magnetic Resonance in Medicine, Volume 70, Issue 5, pages 1192\textendash{}1199, November \textbf{2013}

127. SMOL\'{I}K, Lubo\v{s}, and Michal HAJ ˇZMAN. "MEASUREMENT OF THE LIGHTWEIGHT ROTOR EIGENFREQUENCIES AND TUNING OF ITS MODEL PARAMETERS. Transactions of the VSB \textendash{} Technical University of Ostrava, Mechanical Series ˇ No. 1, \textbf{2013}, vol. LIX article No. 1942

128. Kumssa, Aida Meredassa. "Tablet User Interface Evaluation for a Portable Ultrasound System and Real-time Doppler Spectrum Processing." (\textbf{2013}).

129. Circuit level defects in the developing neocortex of Fragile X mice, J Tiago Gon\c{c}alves, James E Anstey, Peyman Golshani, Carlos Portera-Cailliau, Nature Neuroscience 16, 903\textendash{}909 (\textbf{2013}) doi:10.1038/nn.3415

130. A Baradarani, J Sadler, JRB Taylor, High-resolution blood flow imaging through the skull, Electronics Letters, vol. 40, no. 13, \textbf{2014}, pp. 798\textendash{}799.

131. Singh, R. (\textbf{2014}). Tune Measurement at GSI SIS-18: Methods and Applications (Doctoral dissertation, Technische Universit\"{a}t).

132. Pander, Tomasz, et al. "An automatic saccadic eye movement detection in an optokinetic nystagmus signal." Biomedical Engineering/Biomedizinische Technik 59.6 (\textbf{2014}): 529-543.

133. "Demonstration of Large Coupling-Induced Phase Delay in Silicon Directional Cross-Couplers," Westerveld, W.J.; Pozo, J.; Leinders, S.M.; Yousefi, M.; Urbach, H.P., Selected Topics in Quantum Electronics, IEEE Journal of, vol.20, no.4, pp.1,6, July-Aug. \textbf{2014}, doi: 10.1109/JSTQE.2013.2292874

134. ``Probabilistic peak detection for first-order chromatographic data'', M. Lopatka, G. Vivo-Truyols, M.J. Sjerps, Analytical Chemica Acta, \textbf{2014} DOI: \url{http://dx.doi.org/10.1016/j.aca.2014.02.015}

135. "A recursive algorithm for optimizing differentiation." Mashreghi, Ali, and Hadi Sadoghi Yazdi. Journal of Computational and Applied Mathematics 263 (\textbf{2014}): 1-13.

136. Cade, D. E. (\textbf{2014}). Detection, classification and ecology of acoustic scattering layers (Doctoral dissertation).

137. Grubi\v{s}i\'{c}, Vladimir, et al. "Heterogeneity of myotubes generated by the MyoD and E12 basic helix-loop-helix transcription factors in otherwise non-differentiation growth conditions." Biomaterials 35.7 (\textbf{2014}): 2188-2198.

138. ``Comparison of Signal Smoothing Techniques for Use in Embedded System for Monitoring and Determining the Quality of Biofuels'', Dalton C\'{e}zane Gomes Valadares, Rute Cardoso Drebes, Elmar Uwe Kurt Melcher, S\'{e}rgio de Brito Esp\'{i}nola, Joseana Mac\^{e}do Fechine R\'{e}gis de Ara\'{u}jo, Applied Mechanics and Materials, Vols. 448-453, pages 1679-1688, Trans Tech Publications, Switzerland, \textbf{2014}. DOI: 10.4028/www.scientific.net/AMM.448-453.1679

139. ``Characterization of Integrated Optical Strain Sensors Based on Silicon Waveguides," Westerveld, W.J.; Leinders, S.M.; Muilwijk, P.M.; Pozo, J.; van den Dool, T.C.; Verweij, M.D.; Yousefi, M.; Urbach, H.P., Selected Topics in Quantum Electronics, IEEE Journal of, vol.20, no.4, pp.1,10, July-Aug. \textbf{2014}. doi:

10.1109/JSTQE.2013.2289992

140. ``Gaussian-function-based deconvolution method to determine the penetration ability of petrolatum oil into in vivo human skin using confocal Raman microscopy'', Chun-Sik Choe, J\"{u}rgen Lademann, and Maxim E Darvin, Laser Phys. 24 10560, \textbf{2014}. (\url{http://iopscience.iop.org/1555-6611/24/10/105601})

141. ``Borosilicate Glass Containing Bismuth and Zinc Oxides as a Hot Cell Material for Gamma-Ray Shielding''. H. A. Saudi, H. A. Sallam, K. Abdullah. Physics and Materials Chemistry. \textbf{2014}; 2(1):20-24. doi: 10.12691/pmc-2-1-4.

142. ``Theta-Burst Stimulation of Hippocampal Slices Induces Network-Level Calcium Oscillations and Activates Analogous Gene Transcription to Spatial Learning'', Graham K. Sheridan, Emad Moeendarbary, Mark Pickering, John J. O'Connor, and Keith J. Murphy, PLOS One, June 20, \textbf{2014}. DOI: 10.1371/journal.pone.0100546

143. Mahmoud, Imbaby I., and Mohamed S. El\_Tokhy. "Development of coincidence summing and resolution enhancement algorithms for digital gamma ray spectroscopy." Journal of Analytical Atomic Spectrometry 29.8 (\textbf{2014}): 1459-1466.

144. M. Rahmat, W. Maulina, Isnaeni, Miftah, N. Sukmawati, E. Rustami, M. Azis, K.B. Seminar, A.S. Yuwono, Y.H. Cho, H. Alatas, Development of a novel ozone gas sensor based on sol\textendash{}gel fabricated photonic crystal, Sensors and Actuators A: Physical, Volume 220, 1 December \textbf{2014}, Pages 53\textendash{}61

145. ``Bacteria-instructed synthesis of polymers for self-selective microbial binding and labelling'', E. Peter Magennis,Francisco Fernandez-Trillo,Cheng Sui, Sebastian G. Spain, David J. Bradshaw, David Churchley, Giuseppe Mantovani, Klaus Winzer \& Cameron Alexander, Nature Materials 13, 748\textendash{}755 (\textbf{2014}) doi:10.1038/nmat3949 (\url{http://www.nature.com/nmat/journal/v13/n7/extref/nmat3949-s1.pdf})

146. A COMPUTERIZED DATABASE FOR BULLET COMPARISON BY CONSECUTIVE MATCHING, Ashley Chu, David Read and David Howitt, Federally funded grant report, U.S. Department of Justice, Document No. 247771, July \textbf{2014}. (\url{http://www.crime-scene-investigator.net/computerized-database-for-bullet-comparisonby-consecutive-matching.pdf})

147. Cade David E., Benoit-Bird Kelly J., (\textbf{2014}), An automatic and quantitative approach to the detection and tracking of acoustic scattering layers, Limnology and Oceanography: Methods, 12, doi: 10.4319/lom. \textbf{2014}.12.742.

148. Blake, Phillip, et al. "Diffraction in nanoparticle lattices increases sensitivity of localized surface plasmon resonance to refractive index changes." Journal of Nanophotonics 8.1 (\textbf{2014}): 083084-083084.

149. Sprinkhuizen, Sara M., Jerome L. Ackerman, and Yi Qiao Song. "Influence of -bone marrow composition on measurements of trabecular microstructure using decay due to diffusion in the internal field MRI: Simulations and clinical studies." Magnetic Resonance in Medicine 72.6 (\textbf{2014}): 1499-1508.

150. Canlas, Reich Rechner D., Carlo Noel E. Ochotorena, and Elmer P. Dadios,"Fuzzy-genetic photoplethysmograph peak detection." Humanoid, Nanotechnology, Information Technology, Communication and Control, Environment and Management\textbackslash (HNICEM), 2014 International Conference on. IEEE, \textbf{2014}.

151. Duenas, J. A., et al. "Dependency on the silicon detector working bias for proton\textendash{}deuteron particle identification at low energies." Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment 714 (\textbf{2013}): 48-52.

152. Sterling, Ryan, and Nathaniel Todd. "USING NEURAL SIGNALS TO PROVIDE INPUT FOR COMPUTING APPLICATIONS IN AUTONOMOUS PROSTHETICS." [PDF] from 136.142.82.187

153. Wang, Xiao, Yi-Qing Ni, and Ke-Chang Lin. "Comparison of statistical counting methods in SHM-based reliability assessment of bridges." Journal of Civil Structural Health Monitoring: 1-12.

154. Gonz\'{a}lez-S\'{a}iz, J. M., et al. "Modulation of the phenolic composition and colour of red wines subjected to accelerated ageing by controlling process variables", Food chemistry 165 (\textbf{2014}): 271-281.

155. Kurniawan, Itmy Hidayat, and Sahat Simbolon. "Deteksi dan Pengukuran Spektra dalam Analisis Spektrografi Emisi dengan Pengolahan Citra." Jurnal Nasional Teknik Elektro dan Teknologi Informasi (JNTETI) 3.1 (\textbf{2014}).

156. Souri, Zoha. EEG-BASED ASSESSMENT OF DRIVER’S PERCEPTION OF TRAFFIC ENVIRONMENT. Diss. Lamar University, \textbf{2014}.

157. Lin, Junfang, et al. "Novel method for quantifying the cell size of marine phytoplankton based on optical measurements." Optics express 22.9 (\textbf{2014}): 10467-10476.

158. Hammonds Jr, James S., Kimani A. Stancil, and Charlezetta E. Stokes. "Quality factor temperature dependence of a surface phonon polariton resonance cavity." Applied Physics Letters 105.11 (\textbf{2014}): 114107.

159. Mall, U., et al. "Characterization of lunar soils through spectral features extraction in the NIR." Advances in Space Research 54.10 (\textbf{2014}): 2029-2040.

160. Bucur, R. V. "Structure of the Voltammograms of the Platinum-Black Electrodes: Derivative Voltammetry and Data Fitting Analysis." Electrochimica Acta 129 (\textbf{2014}): 76-84.

161. Teixeira, Carlos Esteves. "Sobre a teoria da difra\c{c}\~{a}o de raios-X em estruturas tridimensionais." (\textbf{2014}). [PDF] from ufmg.br

162. Moon, Jim, et al. "Cable system for generating signals for detecting motion and measuring vital signs." U.S. Patent No. 8,738,118. 27 May \textbf{2014}.

163. Thompson, D. Brian, et al. "A Comparison of R-line Photoluminescence of Emeralds from Different Origins." The Journal of Gemmology 34.4 (\textbf{2014}): 334.

164. Oliveira, Raphael Rocha de. "Modelos de calibra\c{c}\~{a}o multivariada por NIRS para a predi\c{c}\~{a}o de caracter\'{i}sticas de qualidade da carne bovina." (\textbf{2014}). PDF] from ufg.br

165. Kirley, M. P. (\textbf{2014}). Electrical conductivity of metal surfaces at terahertz frequencies (Doctoral dissertation, The University of Wisconsin-Madison).

166. Anderson, Danielle L., et al. "Spatial and temporal distribution of ${\upgamma}$H2AX fluorescence in human cell cultures following synchrotron-generated X-ray microbeams: lack of correlation between persistent ${\upgamma}$H2AX foci and apoptosis. "Synchrotron Radiation 21.4 (\textbf{2014}).

167. Maxfield, Dane Arthur. KINESIN-1 REGULATES SYNAPTIC STRENGTH BY MEDIATING DELIVERY, REMOVAL AND REDISTRIBUTION OF AMPARS. Diss. The

University of Utah, \textbf{2014}.

168. Zou, Xiaoyu, Magneto-optical properties of ferromagnetic nanostructures on modified nanosphere templates. Thesis, CALIFORNIA STATE UNIVERSITY, LONG BEACH, \textbf{2014}, 87 pages; 1591619

169. A Carrasco, TA Brown, SG Lomber, Spectral and Temporal Acoustic Features Modulate Response Irregularities within Primary Auditory Cortex Columns, PloS one, \textbf{2014}, DOI: 10.1371/journal.pone.0114550

170. Sirotin, Yevgeniy B., Mart\'{i}n Elias Costa, and Diego A. Laplagne. "Rodent ultrasonic vocalizations are bound to active sniffing behavior." \textit{Frontiers in behavioral neuroscience} 8 (\textbf{2014}).

171. Luo, Changtong, et al. "Wave system fitting: A new method for force measurements in shock tunnels with long test duration." Mechanical Systems and Signal Processing (\textbf{2015}).

172. Bleecker, J. V. (\textbf{2015}). Relating phase separation and thickness mismatch in model lipid membranes (Doctoral dissertation).

173. M\"{o}bius, Klaus, et al. "M\"{o}bius\textendash{}H\"{u}ckel topology switching in an expanded porphyrin cation radical as studied by EPR and ENDOR spectroscopy." Physical Chemistry Chemical Physics 17.9 (\textbf{2015}): 6644-6652.

174. Tariq, Humera, and SM Aqil Burney. "Low Level Segmentation of Brain MR Slices and Quantification Challenges.", NCMCS'15 (\textbf{2015}). Link.

175. Nystad, Helle Emilia. Comparison of Principal Component Analysis and Spectral Angle Mapping for Identification of Materials in Terahertz Transmission Measurements. Diss. Master’s thesis, Norwegian University of Technology and Science, \textbf{2015}.

176. Hahn, Christian, et al. "Adjusting rheological properties of concentrated microgel suspensions by particle size distribution." \textit{Food Hydrocolloids} 49 (\textbf{2015}): 183-191.

177. Chiuchi\'{u}, D. "Time-dependent study of bit reset." EPL (Europhysics Letters)109.3 (\textbf{2015}): 30002.

178. Taghizadeh, Mohammad Taghi, Nazanin Yeganeh, and Mostafa Rezaei. "The investigation of thermal decomposition pathway and products of poly (vinyl alcohol) by TG FTIR." - \textit{Journal of Applied Polymer Science} 132.25 (\textbf{2015}).

179. P Sevusu, Real-time air quality measurements using mobile platforms, \textbf{2015}, Thesis, [PDF] from rutgers.edu

180. D. S. Khvostichenko, J. D. D. Ng, S. L. Perry, M. Menon, P. J. A. Kenis, Effects of detergent ${\upbeta}$-octyglucoside and phosphate salt solutions on phase behavior of monoolein mesophases, [PDF] from researchgate.net

181. Mahmoud, Imbaby I., and Mohamed S. El\_Tokhy. "Advanced signal separation and recovery algorithms for digital x-ray spectroscopy." \textit{Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment} 773 (\textbf{2015}): 104-113.

182. Morrow, Justin D. Surface Microstructure and Properties of Pulsed Laser Micro Melted S7 Tool Steel. The University of Wisconsin-Madison, \textbf{2015}.

183. Ubnoske, Stephen M., et al. "Role of nanocrystalline domain size on the electrochemical double-layer capacitance of high edge density carbon nanostructures." \textit{MRS Communications} (\textbf{2015}): 1-6.

184. MUHAMMAD MUFTI AZIS, ``Experimental and kinetic studies of H2 effect on lean exhaust after treatment processes: HC-SCR and DOC'' CHALMERS UNIVERSITY OF TECHNOLOGY G\"{o}teborg, Sweden \textbf{2015}

185. Umesh Rudrapatna, S., et al. "Measurement of distinctive features of cortical spreading depolarizations with different MRI contrasts." NMR in Biomedicine 28.5 (\textbf{2015}): 591-600.

186. K\"{u}hbach, Markus, Br\"{u}ggemann, Thiemo, Molodov, Konstantin, Gottstein, G\"{u}nter. ``On a Fast and Accurate In-Situ Measuring Strategy for Recrystallization Kinetics and Its Application to an Al-Fe-Si Alloy'', \textit{Metallurgical and Materials Transactions} A, March \textbf{2015}, Volume 46, Issue 3, pp 1337-1348

187. D. Y. Lipatov, Y. R. Shaltaeva, V. V. Belyakov, A. V. Golovin, V. S. Pershenkov, V. V. Shurenkov, D. Y. Yakovlev, ``Modeling of IMS Spectra in Medical Diagnostic Purposes'', 3rd International Conference on Nanotechnologies and Biomedical Engineering, Volume 55 of the series IFMBE Proceedings, \textbf{2015}, pp 404-408

188. Y. Meerten, Y. Swolfs, J. Baets, L. Gorbatikh, I. Verpoebucurst, ``Penetration impact testing of self-reinforced composites'', Composites Part A: Applied Science and Manufacturing, Volume 68, January \textbf{2015}, Pages 289\textendash{}295

189. Ivanov, I, Optimal filtering of synchronized current phasor measurements in asteady state, 2015 IEEE International Conference on Industrial Technology (ICIT), Pages 1362 - 1367, 17-19 March \textbf{2015}

190. L Farge, J Boisse, J Dillet, S Andr\'{e}, Wide angle X ray scattering study of the lamellar/fibrillar transition for a semi crystalline polymer deformed in tension in relation with the evolution of volume strain\textit{, Journal of Polymer Science} B, Volume 53, Issue 20, 15 October \textbf{2015}, Pages 1470\textendash{}1480

191. Patrick Schloth, Precipitation in the high strength AA7449 aluminium alloy: implications on internal stresses on different length scales, Thesis, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, Lausanne, Switzerland, June \textbf{2015}.

192. Guzman, P. (\textbf{2015}). Studying the Physical Stability of BSA at the Bulk Solution and Oil/Water Interface (Doctoral dissertation, University of Otago).

193. FlavonQ: An Automated Data Processing Tool for Profiling Flavone and Flavonol Glycosides with Ultra-High-Performance Liquid Chromatography\textendash{}Diode Array Detection\textendash{}High Resolution Accurate Mass\textendash{}Mass Spectrometry, Mengliang Zhang, Jianghao Sun, and Pei Chen*, \textit{Anal. Chem}., \textbf{2015}, 87 (19), pp 9974\textendash{}9981,

DOI: 10.1021/acs.analchem.5b02624

194. Schulze, H. Georg, and Robin FB Turner. "Development and Integration of Block Operations for Data Invariant Automation of Digital Preprocessing and Analysis of Biological and Biomedical Raman Spectra." \textit{Applied spectroscopy} 69.6 (\textbf{2015}): 643-664.

195. Hutchison, Richard Stephen. Novel high refractive index, thermally conductive additives for high brightness white LEDs. Diss. Rensselaer Polytechnic Institute, \textbf{2015}.

196. Magnotti, G., et al. "Raman spectra of methane, ethylene, ethane, dimethyl ether, formaldehyde and propane for combustion applications." \textit{Journal of Quantitative Spectroscopy and Radiative Transfer} 163 (\textbf{2015}): 80-101.

197. Chen, Rex Chin-Hao. "Spectral and Temporal Interrogation of Cerebral Hemodynamics Via High-Speed Laser Speckle Contrast Imaging." (\textbf{2015}).

198. Maistry, N. (\textbf{2015}). Investigating the concept of Fraunhofer lines as a potential method to detect corona in the wavelength region 338nm-405nm during the day (Doctoral dissertation).

199. Parker, Michael J. Coupling Nuclear Induced Phonon Propagation with Conversion Electron Moessbauer Spectroscopy. No. AFIT-ENP-MS-15-J-054. AIR FORCE INSTITUTE OF TECHNOLOGY WRIGHT-PATTERSON AFB OH GRADUATE SCHOOL OF ENGINEERING AND MANAGEMENT, \textbf{2015}.

200. Maistry, Nattele. Investigating the concept of Fraunhofer lines as a potential method to detect corona in the wavelength region 338nm-405nm during the day. Diss. \textbf{2015}.

201. Liu, Yanping, et al. "Applications of Savitzky-Golay Filter for Seismic Random Noise Reduction." \textit{Acta Geophysica} (\textbf{2015}).

202. Kojimoto, N. C. (\textbf{2015}). Ultrasonic inspection methods for defect detection and process control in roll-to-roll flexible electronics manufacturing (Doctoral dissertation, Massachusetts Institute of Technology).

203. Sheehan, Terry L., and Richard A. Yost. "What’s the most meaningful standard for mass spectrometry: instrument detection limit or signal-to-noise ratio" \textit{Current Trends Mass Spectrometry} 13 (\textbf{2015}): 16-22.

204. Bleecker, J. V. (\textbf{2015}). Relating phase separation and thickness mismatch in model lipid membranes (Doctoral dissertation).

205. Ilewicz, Witold, et al. "Comparison of baseline estimation algorithms for chromatographic signals." Methods and Models in Automation and Robotics (MMAR), 2015 20th International Conference on. IEEE, \textbf{2015}.

206. Massimi, Federico. Sviluppo di metodi integrati basati sulle tecniche di nanoindentazione e del fascio ionico focalizzato (FIB) per la caratterizzazione, risolta nello spazio, delle propriet\`{a} meccaniche dei materiali", ArcAdiA." (\textbf{2015}). \url{http://hdl.handle.net/2307/5329}

207. Swoboda, Daniel Maximilian, et al. "A Comprehensive Study of Simple Digital Filters for Botball IR Detection Techniques." PDF link.

208. CE Funes, EF Cromwell System and method for determining a baseline measurement for a biological response curve, US Patent App. 13/308,021, 2

209. AD Beyene, R Bluffstone, Z Gebreegziabher, The Improved Biomass Stove Saves Wood, But How Often Do People Use It?, [TXT] from worldbank.com

210. Raunio, Saida. "IMMUNOASSAY TEST FOR A QVANTITATIVE DETERMINATION OF HELICOBACTER PYLORI ANTIBODY IN BLOOD DONORS" (\textbf{2015}). PDFAlt, Daniel M. Design and Commissioning of a 16.1 MHz Multiharmonic Buncher for the ReAccelerator at NSCL. ProQuest, \textbf{2016}.

211. Coy, A., Rankine, D., Taylor, M., Nielsen, D. C., \& Cohen, J. (\textbf{2016}). Increasing the accuracy and automation of fractional vegetation cover estimation from digital photographs. Remote Sensing, 8(7), 474.

212. Nguyen, Tuan Ngoc. "An algorithm for extracting the PPG Baseline Drift in realtime."

(\textbf{2016}). PDF link.

213. Maitre, L\'{e}a. "Metabonomic and epidemiological analyses of maternal parameters and exposures during pregnancy and their influence on fetal growth amongst the INMA birth cohort." (\textbf{2016}). PDF link.

214. Lipatov, D. Y., et al. "Modeling of IMS Spectra in Medical Diagnostic Purposes." 3rd International Conference on Nanotechnologies and Biomedical Engineering. Springer Singapore, \textbf{2016}.

215. Tong, Xia, et al. "Recursive Wavelet Peak Detection of Analytical Signals." Chromatographia 79.19-20 (\textbf{2016}): 1247-1255.

216. Wang, Xing. Effects of Interfaces on Properties of Cladding Materials for Advanced Nuclear Reactors. The University of Wisconsin-Madison, \textbf{2016}. PDF link.

217. Dang, Hue, Marian Dekker, Jason Farquhar, and Tom Heskes. "Processing and analyzing functional near-infrared spectroscopy data." (\textbf{2016}).

218. Damavandi, H. G. (\textbf{2016}). Data analytics, interpretation and machine learning for environmental forensics using peak mapping methods (Doctoral dissertation, The University of Iowa).

219. Gill, Ruby K., et al. "The effects of laser repetition rate on femtosecond laser ablation of dry bone: a thermal and LIBS study." Journal of biophotonics 9.1-2 (\textbf{2016}): 171-180.

220. Performance evaluation and optimization of X-ray stress measurement for nickel aluminium bronze based on the Bayesian method. Journal of Applied Crystallography, \textbf{2016} \textendash{} scripts.iucr.org

221. Top-down modulation of stimulus drive via beta-gamma cross-frequency interaction. CG Richter, WH Thompson, CA Bosman, P Fries - bioRxiv, \textbf{2016} \textendash{} biorxiv.org

222. Azp\'{u}rua, Marco A., Marc Pous, and Ferran Silva. "Decomposition of Electromagnetic Interferences in the Time-Domain." (\textbf{2016}).

223. Barros, Rodrigo Emanoel de Britto Andrade. SISTEMA DE INTERROGA\c{C}\~{A}O DE REDES DE BRAGG: PRIMEIROS PASSOS NA CRIA\c{C}\~{A}O DE UM PROT\'{O}TIPO. Diss. Universidade Federal do Rio de Janeiro, \textbf{2016}.

224. Li, Yuanlu, et al. "A novel signal enhancement method for overlapped peaks with noise immunity." \textit{Spectroscopy Letters} 49.4 (\textbf{2016}): 285-293.

225. Hatterschide, Joshua. "Retroviral-RNA Structure and Function: Investigating the role of aminoacyl-tRNA synthetases and retroviral-RNA structural elements in the initiation of reverse transcription." (\textbf{2016}).

226. Guizani, Chamseddine, et al. "Biomass char gasification by H 2 O, CO 2 and their mixture: Evolution of chemical, textural and structural properties of the chars." Energy 112 (\textbf{2016}): 133-145.

227. Wagner, C. F. (\textbf{2016}). Transition from transparency to hole-boring in relativistic laser-solid interactions at the Texas Petawatt (Doctoral dissertation).

228. Bocaege, E., and S. Hillson. "Disturbances and noise: Defining furrow form enamel hypoplasia." \textit{American journal of physical anthropology} 161.4 (\textbf{2016}): 744-751

229. Merla, Yu, et al. "Extending battery life: A low-cost practical diagnostic technique for lithium-ion batteries." \textit{Journal of Power Sources} 331 (\textbf{2016}): 224-231.

230. Besemer, Matthieu, et al. "Identification of Multiple Water\textendash{}Iodide Species in Concentrated NaI Solutions Based on the Raman Bending Vibration of Water." \textit{The Journal of Physical Chemistry} A 120.5 (\textbf{2016}): 709-714.

231. Cairone, Fabiana, Salvina Gagliano, and Maide Bucolo. "Experimental study on the slug flow in a serpentine microchannel." \textit{Experimental Thermal and Fluid Science} 76 (\textbf{2016}): 34-44.

232. Davison, Adrian K., et al. "Objective Micro-Facial Movement Detection Using FACS-Based Regions and Baseline Evaluation." arXiv preprint arXiv:1612.05038 (\textbf{2016}).

233. Ninh, Giang Nguyen, et al. "Radioisotope identification method for poorly resolved gamma-ray spectrum of nuclear security concern." \textit{AIP Conference Proceedings}. Vol. 1704. No. 1. AIP Publishing, \textbf{2016}.

234. Brachi, Paola, et al. "Pseudo-component thermal decomposition kinetics of tomato peels via isoconversional methods." \textit{Fuel Processing Technology} 154 (\textbf{2016}): 243-250.

235. Lee, Hansol, et al. "Flow suppressed hyperpolarized 13C chemical shift imaging using velocity optimized bipolar gradient in mouse liver tumors at 9.4 T.", \textit{Magnetic resonance in medicine} (\textbf{2016}).

236. Wu, B., et al. "Novel application of differential thermal voltammetry as an in-depth state-of-health diagnosis method for lithium-ion batteries." PDF file.

237. Creese, Andrew J., and Helen J. Cooper. "Separation of cis and trans Isomers of Polyproline by FAIMS Mass Spectrometry." \textit{Journal of The American Society for Mass Spectrometry} 27.12 (\textbf{2016}): 2071-2074.

238. Kvyetnyy, Roman, et al. "Improving the quality perception of digital images using modified method of the eye aberration correction." Photonics Applications in Astronomy, Communications, Industry, and High-Energy Physics Experiments 2016. Vol. 10031. \textit{International Society for Optics and Photonics}, \textbf{2016}.

239. Myers, G. A., Turner, L. G., Morgan, Q., \& Pearce, J., ``Raman Spectroscopy-detecting SOx and NOx in the Precipice Sandstone''. (\textbf{2016})

240. Pancholi, Manthan, et al. "Relative Translation and Rotation Calibration Between Optical Target and Inertial Measurement Unit." International Conference on Sensor Systems and Software. Springer, Cham, \textbf{2016}.

241. Ferriss, Elizabeth, Terry Plank, and David Walker. "Site-specific hydrogen diffusion rates during clinopyroxene dehydration." \textit{Contributions to Mineralogy and Petrology} 171.6 (\textbf{2016}): 55.

242. Roy, Sujan Kumar, Wei-Ping Zhu, and Benoit Champagne. "Single channel speech enhancement using subband iterative Kalman filter." Circuits and Systems (ISCAS), \textbf{2016} IEEE International Symposium on. IEEE, \textbf{2016}.

243. Langaas, Gjertrud Louise. "Measurements of radioactivity in plant and soil samples taken near a nuclear power plant." (\textbf{2016}). PDF link.

244. Benigni, Paolo, and Francisco Fernandez-Lima. "Oversampling selective accumulation trapped ion mobility spectrometry coupled to FT-ICR MS: fundamentals and applications." \textit{Analytical chemistry} 88.14 (\textbf{2016}): 7404-7412.

245. Geiger, Matthew, and Michael T. Bowser. "Effect of fluorescent labels on and amino acid sample dimensionality in two dimensional nLC${\times}$ ${\upmu}$FFE separations." \textit{Analytical chemistry} 88.4 (\textbf{2016}): 2177-2187.

246. Aldokhail, A. M. (\textbf{2016}). Automated Signal to Noise Ratio Analysis for Resonance Imaging Using a Noise Distribution Model (Doctoral dissertation, University of Toledo).

247. Fasching, Joshua, et al. "Automated coding of activity videos from a study." Robotics and Automation (ICRA), 2016 IEEE International Conference. IEEE, \textbf{2016}.

248. Bleecker, J. V., Cox, P. A., Foster, R. N., Litz, J. P., Blosser, M. C., Castner, D. G., \& Keller, S. L. (20\textbf{1}6). Thickness Mismatch of Coexisting Liquid Phases in Non-Canonical Lipid Bilayers. \textit{The journal of physical chemistry}. B, 120(10), 2761.

249. Joshi, Bijal, and Nitu Anil Kumar. "Computationally efficient data rate mismatch compensation for telephony clocks." U.S. Patent No. 9,514,766. 6 Dec. \textbf{2016}.

250. Vallet, Aur\'{e}lien, et al. "A multi-dimensional statistical rainfall threshold for deep landslides based on groundwater recharge and support vector machines." \textit{Natural Hazards} 84.2 (\textbf{2016}): 821-849.

251. Wang, Lili, Paul DeRose, and Adolfas K. Gaigalas. "Assignment of the number of equivalent reference fluorophores to dyed microspheres." \textit{J. Res. Nat. Ins. Stand. Technol}. 121 (\textbf{2016}): 269-286.

252. Skaret, H. B. (\textbf{2016}). The Arctic Sea Ice-Melting During Summer or not Freezing

in Winter? (Master's thesis, The University of Bergen). PDF link.

253. Tuan T. Tran, et. al., Synthesis of Ge1${-}$xSnx alloys by ion implantation and pulsed laser melting: Towards a group IV direct bandgap material, \textit{Journal of Applied Physics} 119(18):183102, \textbf{2016}, DOI: 10.1063/1.4948960

363. Choi, Jae Sung, et al. "A New Automated Cell Counting Program by Using Hough Transform-Based Double Edge." \textit{Advances in Computer Science and Ubiquitous Computing}. Springer, Singapore, \textbf{2016}. 712-716.

253. Van der Rest, Guillaume, Human Rezaei, and Fr\'{e}d\'{e}ric Halgand. "Monitoring Conformational Landscape of Ovine Prion Protein Monomer Using Ion Mobility Coupled to Mass Spectrometry." \textit{Journal of The American Society for Mass Spectrometry} 28.2 (\textbf{2017}): 303-314.

254. Mirsafavi, Rustin Y., et al. "Detection of papaverine for the possible identification of illicit opium cultivation." \textit{Analytical Chemistry} 89.3 (\textbf{2017}): 1684-1688.

255. Myers, Grant A., Kelsey Kehoe, and Paul Hackley. "Analysis of Artificially Matured Shales with Confocal Laser Scanning Raman Microscopy: Applications to Organic Matter Characterization." Unconventional Resources Technology Conference (URTEC), \textbf{2017}.

256. Torres, Andrei BB, Jos\'{e} Adriano Filho, Atslands R. da Rocha, Rubens Sonsol Gondim, and Jos\'{e} Neuman de Souza. "Outlier detection methods and sensor data fusion for precision agriculture", \textbf{2017}, PDF link.

257. Desmet, F., Lesaffre, M., Six, J., Ehrl\'{e}, N., \& Samson, S. (\textbf{2017}). Multimodal analysis of synchronization data from patients with dementia. In ESCOM 2017.

258. Seeber, Renato, and Alessandro Ulrici. "Analog and digital worlds: Part 2. Fourier analysis in signals and data treatment." \textit{ChemTexts} 3.2 (\textbf{2017}): 8.

259. Mustafa, M. A., et al. "Nonintrusive Freestream Velocity Measurement in a Large-Scale Hypersonic Wind Tunnel." \textit{AIAA Journal} (\textbf{2017}).

260. Su\'{a}rez-Cort\'{e}s, Pablo, et al. "Ned-19 inhibition of parasite growth and multiplication suggests a role for NAADP mediated signaling in the asexual development of Plasmodium falciparum." \textit{Malaria Journal} 16.1 (\textbf{2017}): 366.

261. Catalbas, M. C., \& Dobrisek, S., 3D Moving Sound Source Localization via Conventional Microphones. \textit{Elektronika ir Elektrotechnika}, 23(4), 63-69. (\textbf{2017}).

262. Du, Zhenhui, et al. "High-sensitive carbon disulfide sensor using wavelength modulation spectroscopy in the mid-infrared fingerprint region." \textit{Sensors and Actuators B: Chemical} 247 (\textbf{2017}): 384-391.

263. Hamilton, N. E., Mahjoub, R., Laws, K. J., \& Ferry, M. (\textbf{2017}). A blended NPT/NVT scheme for simulating metallic glasses. \textit{Computational Materials Science}, 130, 130-137.

264. Sun, Y. C., Huang, C., Xia, G., Jin, S. Q., \& Lu, H. B. (\textbf{2017}). Accurate wavelength calibration method for compact CCD spectrometer. JOSA A, 34(4), 498-\textbackslash 505.

265. Mikhailov, I. F., et al. "Rapid diagnostics of urinary iodine using a portable EDXRF spectrometer." \textit{Journal of X-Ray Science and Technology} Preprint (\textbf{2017}): 1-7. PDF link.

266. Bianchi, Davide, et al. "A wavelet filtering method for cumulative gamma spectroscopy used in wear measurements." Applied Radiation and Isotopes 120 (\textbf{2017}): 51-59.

267. Xiong, Zheng, et al. "Automated Phase Segmentation for Large-Scale X-ray Diffraction Data Using a Graph-Based Phase Segmentation (GPhase) Algorithm." ACS Combinatorial Science 19.3 (\textbf{2017}): 137-144

268. Jim\'{e}nez-Carvajal, C., et al. "Weighing lysimetric system for the determination of the water balance during irrigation in potted plants." Agricultural Water Management 183 (\textbf{2017}): 78-85.

269. Acciarri, R., et al. "Noise Characterization and Filtering in the MicroBooNE Liquid Argon TPC." arXiv preprint arXiv:1705.07341 (\textbf{2017}). PDF link.

270. Mathault, Jessy, Hamza Landari, Frederic Tessier, Paul Fortier, and Amine Miled. "Biological Modeling Challenges in a Multiphysics Approach." Circuits and Systems (MWSCAS), \textbf{2017} IEEE 60th International Midwest Symposium

271. Weiss, Charles J. "Scientific Computing for Chemists: An Undergraduate Course in Simulations, Data Processing, and Visualization." Journal of Chemical Education 94.5 (\textbf{2017}): 592-597.

272. Kianifar, Rezvan, et al. "Automated Assessment of Dynamic Knee Valgus and Risk of Knee Injury During the Single Leg Squat." \textit{IEEE Journal of Translational Engineering in Health and Medicine} 5 (\textbf{2017}): 1-13.

273. Willem deGroot, A., et al. "Molecular Structural Characterization of Polyethylene." Handbook of Industrial Polyethylene and Technology: Definitive Guide to Manufacturing, Properties, Processing, Applications and Markets (\textbf{2017}): 139.

274. Mertens, Andreas, and Josef Granwehr. "Two-dimensional impedance data analysis by the distribution of relaxation times\textit{." Journal of Energy Storage} 13 (\textbf{2017}): 401-408.

275. Wu, Yingwen, and Long Chen. "Comparison of spectra processing methods for SERS based quantitative analysis." Information, Cybernetics and Computational Social Systems (ICCSS), 2017 4th International Conference on. IEEE, \textbf{2017}.

276. Dehnavi, Sahar, Yasser Maghsoudi, and Mohammadjavad Valadanzoej. "Using spectrum differentiation and combination for target detection of minerals." \textit{International Journal of Applied Earth Observation and Geoinformation} 55 (\textbf{2017}): 9-20.

278. Jia, Zhenhua, et al. "HB-phone: a bed-mounted geophone-based heartbeat monitoring system: demo abstract." Proceedings of the 16th ACM/IEEE International Conference on Information Processing in Sensor Networks. ACM, \textbf{2017}.

279. Goz\'{e}, Perrine, et al. "Effects of ozone treatment on the molecular properties of wheat grain proteins." Journal of Cereal Science 75 (\textbf{2017}): 243-251.

280. Giron-Sierra, Jose Maria. "Periodic Signals." Digital Signal Processing with Matlab Examples, Volume 1. Springer Singapore, \textbf{2017}. 3-28.

281. Shojaosadati, Seyed Abbas, Sajjad Naeimipour, and Ahmad Fazeli. "FTIR Investigation of secondary structure of Reteplase inclusion bodies produced in Escherichia coli in terms of urea concentration (Spring 2017)." \textit{Iranian Journal of Pharmaceutical Research} (\textbf{2017}).

282. Peng, Jiyu, et al. "Rapid Identification of Varieties of Walnut Powder Based on Laser-Induced Breakdown Spectroscopy." (\textbf{2017}): 19-28. Abstract.

283. Sun, Lili, et al. "Comprehensive evaluation of chemical stability of Xuebijing injection based on multiwavelength chromatographic fingerprints and multivariate chemometric techniques." \textit{Journal of Liquid Chromatography \& Related Technologies} 40.14 (\textbf{2017}): 715-724.

284. Thompson, D. Brian, et al. "Photoluminescence Spectra of Emeralds from Colombia, Afghanistan, and Zambia." \textit{Gems \& Gemology} 53.3 (\textbf{2017}): 296-311.

285. Choorat, P., et al. "Applied integral intensity projection to find the numbers of the parking spots." Knowledge and Smart Technology (KST), \textbf{2017} 9th International Conference on. IEEE, 2017.

286. Phillips, James William, and Yi Jin. "Devices and methods of low frequency magnetic stimulation therapy." U.S. Patent No. 9,649,502. 16 May \textbf{2017}.

287. Augustyns, Val\'{e}rie, et al. "Evidence of tetragonal distortion as the origin of the ferromagnetic ground state in ${\upgamma}$ ${-}$ Fe nanoparticles." \textit{Physical Review} B 96.17 (\textbf{2017}):174410.

288. Sprague-Klein, Emily A., et al. "Observation of Single Molecule Plasmon-Driven Electron Transfer in Isotopically Edited 4, 4-Bipyridine Gold Nanosphere Oligomers." \textit{Journal of the American Chemical Society} 139.42 (\textbf{2017}): 15212-15221.

289. Mohan, Varun, and Prashant K. Jain. "Spectral Heterogeneity of Hybrid Lead Halide Perovskites Demystified by Spatially Resolved Emission." \textit{The Journal of Physical Chemistry} C121.35 (\textbf{2017}): 19392-19400.

290. Cuss, Chad W., Iain Grant-Weaver, and William Shotyk. "AF4-ICPMS with the 300 Da Membrane to Resolve Metal-Bearing ``Colloids''{\textless} 1 kDa: Optimization, Fractogram Deconvolution, and Advanced Quality Control." \textit{Analytical Chemistry} 89.15 (\textbf{2017}): 8027-8035.

291. Shi, Xiaoyu, et al. "Super-Resolution Microscopy Reveals That Disruption of Ciliary Transition Zone Architecture Is a Cause of Joubert Syndrome." bioRxiv (\textbf{2017}): 142042.

292. Robinson, M. T., et al. "Photocatalytic photosystem I/PEDOT composite films prepared by vapor-phase polymerization." \textit{Nanoscale} 9.18 (\textbf{2017}): 6158-6166.

293. Ros Mart\'{i}, Marc. Deep convolutional neural network architecture for effective Image analysis. MS thesis. Universitat Polit\`{e}cnica de Catalunya, \textbf{2017}.

294. Jackson, Philip J., et al. "Identification of protein W, the elusive sixth subunit of the Rhodopseudomonas palustris reaction center-light harvesting 1 core complex." \textit{Biochimica et Biophysica Acta} (BBA)-Bioenergetics (\textbf{2017}).

295. Johnson, Alexander C., and Michael T. Bowser. "High-Speed, Comprehensive, Two Dimensional Separations of Peptides and Small Molecule Biological Amines Using Capillary Electrophoresis Coupled with Micro Free Flow Electrophoresis." \textit{Analytical chemistry} 89.3 (\textbf{2017}): 1665-1673.

296. Toose, Peter, et al. "Radio-frequency interference mitigating hyperspectral L band radiometer." \textit{Geoscientific Instrumentation, Methods and Data Systems} 6.1 (\textbf{2017}): 39.

297. Pajankar, Ashwin. "Filters and Their Application." Raspberry Pi Image Processing Programming. Apress, \textbf{2017}. 99-110.

298. Taraszewski, Micha\l{}, and Janusz Ewertowski. "Complex experimental analysis of rifle-shooter interaction." Defence Technology (\textbf{2017}).

299. Manlises, Cyrel Ontimare, et al. "Characterization of an ISFET with Built-in Calibration Registers through Segmented Eight-Bit Binary Search in Three-Point Algorithm Using FPGA." \textit{Journal of Low Power Electronics and Applications} 7.3 (\textbf{2017}):19.

300. Kim, Geonha, et al. "Soil sampling strategies for site assessments in petroleum contaminated areas." Environmental geochemistry and health 39.2 (\textbf{2017}): 293-305.

301. Lanevski, Dmitri, Koit Mauring, and Eric Tkaczyk. "Interference filter tilting to detect a polycyclic aromatic hydrocarbon at the second harmonic of wavelength modulation frequency." Applied Optics 56.11 (\textbf{2017}): 3155-3161.

302. Hong, Tae-Kee, Iason Rusodimos, and Myung-Hoon Kim. "Higher order derivative voltammetry for reversible and irreversible electrode processes under spherical diffusion." Journal of Electroanalytical Chemistry 785 (\textbf{2017}): 255-264.

303. Root, Katharina, et al. "Insight into Signal Response of Protein Ions in Native ESI-MS from the Analysis of Model Mixtures of Covalently Linked Protein Oligomers." Journal of The American Society for Mass Spectrometry (\textbf{2017}): 1-13.

304. Du, Zhenhui, et al. "High-sensitive carbon disulfide sensor using wavelength Modulation spectroscopy in the mid-infrared fingerprint region." Sensors and Actuators B: Chemical 247 (\textbf{2017}): 384-391.

305. Elzanfaly, Eman S., et al. "Zero and second derivative synchronous fluorescence spectroscopy for the quantification of two non-classical ${\upbeta}$ lactams in pharmaceutical vials: Application to stability studies." Luminescence (\textbf{2017}).

306. Ferraz de Menezes, Rebeca, et al. "Fs laser ablation of teeth is temperature limited and provides information about the ablated components." Journal of Biophotonics (\textbf{2017}).

307. Huang, Yi-Fan, et al. "Label-free, ultrahigh-speed, 3D observation of bidirectional and correlated intracellular cargo transport by coherent brightfield microscopy." \textit{Nanoscale} 9.19 (\textbf{2017}): 6567-6574.

308. Mahmud, Akib. "Hardware in the Loop (HIL) Rig Design and Electrical Architecture." (\textbf{2017}). 

309. Beyerl, Thomas, et al. \textit{Reducing Complexity in Routing of Non-Standard Intersections, to Aid in Autonomous Vehicle Navigation}. No. 2017-01-0103. SAE Technical Paper, \textbf{2017}.

310. Lee, Hansol, et al. "Flow-suppressed hyperpolarized 13C chemical shift imaging using velocity-optimized bipolar gradient in mouse liver tumors at 9.4 T." \textit{Magnetic resonance in medicine} 78.5 (\textbf{2017}): 1674-1682.

311. Haines, Grant E., and S. Laurie Sanderson. "Integration of swimming kinematics and ram suspension feeding in a model American paddlefish, Polyodon spathula." \textit{Journal of Experimental Biology} (\textbf{2017}): jeb-166835.

312. Zhang, Huajun, and Y. I. N. G. Ning. "Method for Analyzing Mixture Components." U.S. Patent Application 15/120,974, filed March 2, \textbf{2017}.

313. Soto Morras, Marta. "Implementation and Analysis of Real Time Optical Flow Solutions for GPU architectures." (\textbf{2017}).

314. Pajankar, Ashwin. \textit{Raspberry Pi Image Processing Programming}. Apress, \textbf{2017}.

315. Vintila, Florentin, Thomas C. K\"{u}bler, and Enkelejda Kasneci. "Pupil response as an indicator of hazard perception during simulator driving." \textit{Journal of Eye Movement Research} 10.4 (\textbf{2017}): 3.

316. Humera Tariq, Abdul Muqeet, S.M.Aqil Burney, Humera Azam, ``Otsu’s Segmentation{\ldots}.'', \textit{J. Theoretical and Applied Information Technology}, Vol.95. No 22, \textbf{2017}

317 Liu, Yu, et al. "Supersonic transient magnetic resonance elastography for quantitative assessment of tissue elasticity." \textit{Physics in Medicine \& Biology} 62.10 (\textbf{2017}): 4083.

318. Manar M. Ouda, et. Al., Development of Pileup Recovery Algorithms by Peak Detection Method of Digital Gamma Ray Spectroscopy, 34th National Radio Science Conference (NRSC), \textbf{2017}. \href{https://www.researchgate.net/publication/315865878\_Development\_of\_pileup\_recovery\_algorithms\_by\_peak\_detection\_method\_of\_digital\_gamma\_ray\_spectroscopy}{Link to full paper}.

319. Xu, Jun-Li, Aoife A. Gowen, and Da-Wen Sun. "Time series hyperspectral chemical imaging (HCI) for investigation of spectral variations associated with water and plasticizers in casein-based biopolymers." Journal of Food Engineering 218 (\textbf{2018}): 88-105.

320. Smith, Brad C., Bachana Lomsadze, and Steven T. Cundiff. "Optimum repetition rates for dual-comb spectroscopy." \textit{Optics express} 26.9 (\textbf{2018}): 12049-12056.

321. Butler, C. W., et al. "Neurons Specifically Activated by Fear Learning in Lateral Amygdala Display Increased Synaptic Strength." \textit{eNeuro} 5.3 (\textbf{2018}).

322. Pukhlyakova, Ekaterina, et al. "${\upbeta}$-Catenin\textendash{}dependent mechanotransduction dates back to the common ancestor of Cnidaria and Bilateria." \textit{Proceedings of the National Academy of Sciences} 115.24 (\textbf{2018}): 6231-6236. 

323. Cheng, Jie. \textit{Peak Detection to Count Gold Nanoparticles Translocations in Nanopipette}. Diss. UC Santa Cruz, \textbf{2018}. 

324. Bonde, Amelie, et al. "VVRRM: Vehicular Vibration-Based Heart RR-Interval Monitoring System. "\textit{Proceedings of the 19th International Workshop on Mobile Computing Systems \& Applications}. ACM, \textbf{2018}. 

335. Paige, Cristen, et al. "Characterizing the Normative Voice Tremor Frequency in Essential Vocal Tremor." \textit{JAMA Otolaryngology\textendash{}Head \& Neck Surgery} (\textbf{2018}). 

326. Myers, Grant A., Kelsey Kehoe, and Paul Hackley. "Development of Raman Spectroscopy as a Thermal Maturity Proxy in Unconventional Resource Assessment." \textit{Unconventional Resources Technology Conference, Houston, Texas, 23-25 July 2018}. Society of Exploration Geophysicists, American Association of Petroleum Geologists, Society of Petroleum Engineers, \textbf{2018}.

327. Taraszewski, Michal, and Janusz Ewertowski. "Small-Caliber Grenade Projectile Applicable to Individual Grenade Launchers." \textit{Defence Science Journal} 68.5 (\textbf{2018}). 

328. Trinh, N. D., et al. "Double differential neutron spectra generated by the interaction of a 12 MeV/nucleon 36S beam on a thick natCu target." \textit{Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment} 896 (\textbf{2018}): 152-164.

329. Swainsbury, David JK, et al. "Probing the local lipid environment of the Rhodobacter sphaeroides cytochrome bc1 and Synechocystis sp. PCC 6803 cytochrome b6f complexes with styrene maleic acid." \textit{Biochimica et Biophysica Acta (BBA)-Bioenergetics} 1859.3 (\textbf{2018}): 215-225.

330. Reynes, Julien, et al. "Experimental constraints on hydrogen diffusion in garnet." \textit{Contributions to Mineralogy and Petrology} 173.9 (\textbf{2018}): 69.

331. Omer, Muhammad, and Elise C. Fear. "Automated 3D method for the construction of flexible and reconfigurable numerical breast models from MRI scans." \textit{Medical \& biological engineering \& computing} 56.6 (\textbf{2018}): 1027-1040.

332. Klein, Tobias, et al. "Influence of Liquid Structure on Fickian Diffusion in Binary Mixtures of n-Hexane and Carbon Dioxide Probed by Dynamic Light Scattering, Raman Spectroscopy, and Molecular Dynamics Simulations." \textit{The Journal of Physical Chemistry B} (\textbf{2018}).

333. Kielar, A., T. Deschamps, R. Jokel, and J. A. Meltzer. "Abnormal language-related oscillatory responses in primary progressive aphasia." \textit{NeuroImage: Clinical} 18 (\textbf{2018}): 560-574.

334. Prodanov, Milana, et al. "Software Module for Processing EEG Signals in a Biofeedback Based System." \textit{2018 Zooming Innovation in Consumer Technologies Conference (ZINC)}. IEEE, \textbf{2018}.

335. Fratini, Marta, et al. "Surface Immobilization of Viruses and Nanoparticles Elucidates Early Events in Clathrin-Mediated Endocytosis." \textit{ACS infectious diseases} (\textbf{2018}).

336. Sili\c{n}\v{s}, Kaspars. \textit{Plasma Enhanced Chemical-and Physical-Vapor Depositions Using Hollow Cathodes}. Diss. Acta Universitatis Upsaliensis, \textbf{2018}.

337 Schito, Andrea, and Sveva Corrado. "An automatic approach for characterization of the thermal maturity of dispersed organic matter Raman spectra at low diagenetic stages." \textit{Geological Society, London, Special Publications} 484 (\textbf{2018}): SP484-5.

338. Krystal T. Vasquez, et. al., Low-pressure gas chromatography with chemical ionization mass

Spectrometry for quantification of multifunctional organic compounds in the atmosphere, \textit{Atmos. Meas. Tech}. \textbf{2018}. \href{https://www.atmos-meas-tech-discuss.net/amt-2018-223/amt-2018-223.pdf}{PDF}.

339. Pushkarsky, I., Tseng, P., Black, D., France, B., Warfe, L., Koziol-White, C. J., ... \& Damoiseaux, R. (2018). Elastomeric sensor surfaces for high-throughput single-cell force cytometry (vol 2, pg 124, \textbf{2018}).

340. Ismail, Omar, et al. "The Way to Ultrafast, High-Throughput Enantioseparations of Bioactive Compounds in Liquid and Supercritical Fluid Chromatography." \textit{Molecules} 23.10 (\textbf{2018}): 2709.

338. Hellinghausen, Garrett, M. Farooq Wahab, and Daniel W. Armstrong. "Improving visualization of trace components for quantification using a power law-based integration approach." \textit{Journal of Chromatography A} 1574 (\textbf{2018}): 1-8.

339. Khundadze, Nana, et al. "On our way to sub-second separations of enantiomers in high-performance liquid chromatography." \textit{Journal of Chromatography A} 1572 (\textbf{2018}): 37-43.

344. Roy, Daipayan, et al. "Frontiers in Ultrafast Chiral Chromatography." \textit{LC{\textbullet} GC Europe} (\textbf{2018}): 308.

345. Maddalena, Riccardo, Christopher Hall, and Andrea Hamilton. "Effect of silica particle size on the formation of calcium silicate hydrate using thermal analysis." \textit{Thermochimica Acta} (\textbf{2018}).

346. Darweesh, Samar Ahmed, et al. "Advancement and Validation of New Derivative Spectrophotometric Method for Individual and Simultaneous Estimation of Diclofenac sodium and Nicotinamide." \textit{Oriental Journal of Chemistry} 34.3 (\textbf{2018}).

347. Li, Yuanlu, and Min Jiang. "Spatial-fractional order diffusion filtering." \textit{Journal of Mathematical Chemistry} 56.1 (\textbf{2018}): 257-267.

348. Huang, Dian, et al. "High-Speed Live-Cell Interferometry: A New Method for Quantifying Tumor Drug Resistance and Heterogeneity." \textit{Analytical chemistry} 90.5 (\textbf{2018}): 3299-3306.

349. Wu, Rihan, et al. "Demonstration of time-of-flight technique with all-optical modulation and MCT detection in SWIR/MWIR range." \textit{Emerging Imaging and Sensing Technologies for Security and Defence III; and Unmanned Sensors, Systems, and Countermeasures}. Vol. 10799. International Society for Optics and Photonics, \textbf{2018}.

350. Pontremoli, Carlotta, et al. "Insight into the interaction of inhaled corticosteroids with human serum albumin: A spectroscopic-based study." \textit{Journal of pharmaceutical analysis} 8.1 (\textbf{2018}): 37-44.

351. Zhao, Chenjiang. \textit{Signal Processing: Peak Detection}. Diss. UC Santa Cruz, \textbf{2018}.

352. Coelho, Alan A. "Deconvolution of instrument and K${\upalpha}$2 contributions from X-ray powder diffraction patterns using nonlinear least-squares with penalties." \textit{Journal of Applied Crystallography} 51.1 (\textbf{2018}): 112-123.

353. Al-gawwam, Sarmad, and Mohammed Benaissa. "Robust Eye Blink Detection Based on Eye Landmarks and Savitzky\textendash{}Golay Filtering." \textit{Information} 9.4 (\textbf{2018}): 93.

354. Yilmaz, Cagatay Murat, Cemal Kose, and Bahar Hatipoglu. "A Quasi-probabilistic distribution model for EEG Signal classification by using 2-D signal representation." \textit{Computer methods and programs in biomedicine} 162 (\textbf{2018}): 187-196.

355. Gou, Yonggang, et al. "Motion parameter estimation and measured data correction derived from blast-induced vibration: new insights." \textit{Measurement} (\textbf{2018}).

356. Hakala, Teemu, et al. "Direct Reflectance Measurements from Drones: Sensor Absolute Radiometric Calibration and System Tests for Forest Reflectance Characterization." \textit{Sensors (Basel, Switzerland)} 18.5 (\textbf{2018}).

357. Mih\'{a}lik, A., R. \v{D}urikovi\v{c}, and M. Sej\v{c}. "Application of Motion Capture Attributes to Individual Identification under Corridor Surveillance." \textit{Journal of Applied Mathematics, Statistics and Informatics} 14.1 (\textbf{2018}): 37-56.

358. Kianifar, Rezvan, and Dana Kulic. "Automatic assessment of the squat quality and risk of knee injury in the single leg squat." U.S. Patent Application 15/826,259, filed October 11, \textbf{2018}.

359. Parziale, Nick J., et al. "Amplification and Structure of Streamwise-Velocity Fluctuations in Four Shock-Wave/Turbulent Boundary-Layer Interactions." \textit{2018 Fluid Dynamics Conference}. \textbf{2018}.

360. Simon, David M., and Mark T. Wallace. "Integration and Temporal Processing of Asynchronous Audiovisual Speech" \textit{Journal of cognitive neuroscience} 30.3 (\textbf{2018}): 319-337.

361. Richter, Craig G., Richard Coppola, and Steven L. Bressler. "Top-down beta oscillatory signaling conveys behavioral context in early visual cortex." \textit{Scientific reports} 8.1 (\textbf{2018}): 6991.

362. Din\c{c}, Erdal, and Zehra Yazan. "Wavelet transform-based UV spectroscopy for pharmaceutical analysis" \textit{Frontiers in Chemistry} 6 (\textbf{2018}).

363. Bartussek, Jan, and Fritz-Olaf Lehmann. "Sensory processing by motoneurons: a numerical model for low-level flight control in flies." \textit{Journal of The Royal Society Interface} 15.145 (\textbf{2018}): 20180408.

364. Ben Hendrickson, Ralf Widenhorn, Paul R. DeStefano and Erik Bodegom, Detection and Reconstruction of Random Telegraph Signals Using Machine Learning, \textit{Image Processing (ICIP),} Athens, 2018, pp. 2441-2445. \href{https://static1.squarespace.com/static/5cc5cf7eda50d357e986b6f0/t/5cddf6dc4d9e75000152d53a/1558050526419/ML+IEEE+Hendrickson.pdf}{Link}.

365. Oeltzschner, Georg, et al. "Hadamard editing of glutathione and macromolecule-suppressed GABA." \textit{NMR in Biomedicine} 31.1 (\textbf{2018}): e3844.

364. Nocco, Mallika A., Matthew D. Ruark, and Christopher J. Kucharik. "Apparent electrical conductivity predicts physical properties of coarse soils." \textit{Geoderma} 335 (\textbf{2019}): 1-11.

366. \begin{otherlanguage*}{russian}
Лубов, Д. П., М. В. Катков, and Ю. В. Першин. "Вольт\textendash{}амперные характеристики коммерческих сегнетоэлектрических конденсаторов: отклонения от модели Прейзаха."
\end{otherlanguage*} \textarmenian{ՀՀ ԳԱԱ Տեղեկագիր. Ֆիզիկա}  53.1 (\textbf{2018}): 86-95. (Machine translation: Voltage \textendash{} ampere characteristics of commercial ferroelectric capacitors: deviations from the Preisach model. Armenian NAS RA Bulletin: Physics).

367. Thanos Papanicolaou, Achilleas G. Tsakiris, Micah A Wyssmann, Casey Kramer, Boulder Array Effects on Bedload Pulses and Depositional Patches, \textit{Journal of Geophysical Research: Earth Surface 123(11),} \textbf{2018}.

368. Manuja Sharma, et. al., ``Optical pH measurement system using a single fluorescent dye for assessing susceptibility to dental caries'', \textit{Journal of Biomedical Optics} 24(01):1, \textbf{2019}.

369. Mustafa, Muhammad A., David Shekhtman, and Nick J. Parziale. "Single-Laser Krypton Tagging Velocimetry Investigation of Supersonic Air and N 2 Boundary-Layer Flows over a Hollow Cylinder in a Shock Tube." \textit{Physical Review Applied} 11.6 (\textbf{2019}): 064013.\href{https://www.researchgate.net/publication/333677717\_Single-Laser\_Krypton\_Tagging\_Velocimetry\_Investigation\_of\_Supersonic\_Air\_and\_N2\_Boundary-Layer\_Flows\_over\_a\_Hollow\_Cylinder\_in\_a\_Shock\_Tube}{Link}.

370. Karl Auerswald, Franziska K. Fischer, Tanja Winterrath, Robert Brandhuber, ``Rain erosivity map for Germany derived from contiguous radar rain data'', \textit{Hydrology and Earth System Sciences} 23(4):1819-1832, 

April \textbf{2019}, DOI: 10.5194/hess-23-1819-2019

371. Martin Leblanc, et. al., Actinide mixed oxide conversion by advanced thermal denitration route, \textit{Journal of Nuclear Materials} 519:157-165, March \textbf{2019}, DOI: 10.1016/j.jnucmat.2019.03.049

372. Sujan Kumar Roy and Kuldip K. Paliwal, An Iterative Kalman Filter with Reduced-Biased Kalman Gain for Single Channel Speech Enhancement in Non-stationary Noise Condition, \textit{International Journal of Signal Processing Systems} Vol. 7, No. 1, March \textbf{2019}. DOI: 10.18178/ijsps.7.1.7-13

373. J. Chen, C. Yang, H. Zhu \& Y. Li, Adaptive signal enhancement for overlapped peaks based on weighting factor selection, \textit{Spectroscopy Letters}, Volume 52, \textbf{2019}. DOI: 10.1080/00387010.2018.1556219

374. Delfino, I., S. Cavella, and M. Lepore. "Scattering-based optical techniques for olive oil characterization and quality control." \textit{Journal of Food Measurement and Characterization} 13.1 (\textbf{2019}): 196-212.

375. Zhang, G. W., et al. "Decomposition of overlapped ion mobility peaks by sparse representation. "\textit{International Journal of Mass Spectrometry} 436 (\textbf{2019}): 147-152.

376. Demetriou, Demetris. \textit{An Investigation into Nonlinear Random Vibrations based on Wiener Series Theory}. Diss. University of Cambridge, \textbf{2019}.

377. McLaren, Timothy I., Ren\'{e} Verel, and Emmanuel Frossard. "The structural composition of soil phosphomonoesters as determined by solution 31P NMR spectroscopy and transverse relaxation (T2) experiments." \textit{Geoderma} 345 (\textbf{2019}): 31-37.

378. Yan, Qi, Rui Yang, and Jiwu Huang. "Detection of Speech Smoothing on Very Short Clips." \textit{IEEE Transactions on Information Forensics and Security} (\textbf{2019}).

379. Zhang, Weifang, et al. "The Analysis of FBG Central Wavelength Variation with Crack Propagation Based on a Self-Adaptive Multi-Peak Detection Algorithm." \textit{Sensors} 19.5 (\textbf{2019}): 1056.

380. Fayolle, Clemence, M\'{e}lody Labrune, and Jean-Philippe Berteau. "Raman spectroscopy investigation shows that mineral maturity is greater in CD-1 than in C57BL/6 mice distal femurs after sexual maturity." \textit{Connective Tissue Research} (\textbf{2019}).

381. Catlow, C. Richard A., et al. "Synthesis, characterisation and water-gas shift activity of nano-particulate mixed-metal (Al, Ti) cobalt oxides.", \textbf{2019}. \textcolor{color-24}{researchgate.net.}

383. Hansen, Lars N., et al. "Low-temperature plasticity in olivine: Grain size, strain hardening, and the strength of the lithosphere." \textit{Journal of Geophysical Research: Solid Earth} (\textbf{2019}).

384. Shao, Xueguang, et al. "High order derivative to investigate the complexity of the near infrared spectra of aqueous solutions." \textit{Spectrochimica Acta Part A: Molecular and Biomolecular Spectroscopy} 213 (\textbf{2019}): 83-89.

385. Choresh, Yael, et al. "Long-term griffon vulture population dynamics at Gamla Nature Reserve." \textit{The Journal of Wildlife Management} 83.1 (\textbf{2019}): 135-144.

386. DeFelice, Mialy M., et al. "NF-${\upkappa}$B signaling dynamics is controlled by a dose-sensing autoregulatory loop." \textit{Sci. Signal.}12.579 (\textbf{2019}): eaau3568. \href{https://stke.sciencemag.org/content/12/579/eaau3568/tab-pdf}{PDF}.

387. Xiaoxiao Ge, et al., Mechanism studies and fabrication for the incorporation of carbon into Al alloys by the electro-charging assisted process, \textit{Carbon}. \textcolor{color-25}{Page: 203-212,} April \textbf{2019}. DOI: 10.1016/j.carbon.2019.04.049

388. Natalia Molinero. Et. al, ``The human gallbladder microbiome is related to the physiological state and the biliary metabolic profile'', \textit{Microbiome} 7(1), \textbf{2019}. DOI: 10.1186/s40168-019-0712-8

389. Ci Song and Tao Pei, ``Decomposition of Repulsive Clusters in Complex Point Processes with Heterogeneous Components'', \textit{International Journal of Geo-Information 8(8):326,} \textbf{\textit{2019}}\textit{. DOI: 10.3390/ijgi8080326}

390. Stephanie Zaleski, et. al., ``Application of Fiber Optic Reflectance Spectroscopy for the Detection of Historical Glass Deterioration'', \textit{Journal of the American Ceramic Society,} June \textbf{2019}. DOI: 10.1111/jace.16703

391. M A Mustafa and Nick Parziale, ``Proper Orthogonal Decomposition of Streamwise-Velocity Fluctuations in a Compression-Corner Shock-Wave/Turbulent Boundary-Layer Interaction'', Conference: 32nd International Symposium on Shock Waves (ISSW32), June \textbf{2019}, DOI: 10.3850/978-981-11-2730-4\_0473-cd

392. Antonio Matus-Vargas, et. al, ``Aerodynamic Disturbance Rejection Acting on a Quadcopter Near Ground'', 

Conference: 2019 6th International Conference on Control, Decision and Information Technologies (CoDIT), March \textbf{2019}. DOI: 10.1109/CoDIT.2019.8820321

393. Wenqi Cai, ``Modeling and Experimental Study of the Vibration Effects in Urban Free-Space Optical Communication Systems'', \textit{IEEE Photonics Journal} PP(99):1-1, October \textbf{2019}. DOI: 10.1109/ JPHOT.2019.2945695

394. Wei, Lingxiao, et al. "I know what you see: Power side-channel attack on convolutional neural network accelerators." Proceedings of the 34th Annual Computer Security Applications Conference. ACM, \textbf{2018}.

395. Shewcraft, Ryan A., et al. "Coherent neuronal dynamics driven by optogenetic stimulation in the primate brain." \textit{bioRxiv} (\textbf{2019}): 437970.

396. Burke, I. V., and William Johan. "A robust and automated deconvolution algorithm of peaks in spectroscopic data." (\textbf{2019}).

397. Tu, Shen, et al. "Enhanced Formation of Solvent-Shared Ion Pairs in Aqueous Calcium Perchlorate Solution toward Saturated Concentration or Deep Supercooling Temperature and Its Effects on the Water Structure." \textit{The Journal of Physical Chemistry B} 123.45 (\textbf{2019}): 9654-9667.

398. Noori, Ansara, et al. "Portable Device for Continuous Sensing with Rapidly Pulsed LEDs\textendash{}Part 1: Rapid On-the-fly Processing of Large Data Streams using an Open Source Microcontroller with Field Programmable Gate Array." \textit{Measurement} (\textbf{2019}).

399. Kim, Tae Hyong, et al. "Machine learning-based pre-impact fall detection model to discriminate various types of fall." \textit{Journal of biomechanical engineering} 141.8 (\textbf{2019}): 081010.

400. Suresh, P. S., Niranjan Kumar Sura, and K. Shankar. "Landing Response Analysis on High-Performance Aircraft Using Estimated Touchdown States." \textit{SAE International Journal of Aerospace} 12.1 (\textbf{2019}): 23-40.

401. Muirhead, David K., et al. "Raman Spectroscopy: an effective thermal marker in low temperature carbonaceous fold-thrust belts." \textit{Geological Society, London, Special Publications} 490 (\textbf{2019}): SP490-2019.

402. Moreira, Mateus Perris\'{e}, Manuel Castro Carneiro, and Andrey Linhares Bezerra de Oliveira. "Desenvolvimento de um programa para modelagem da curva de titula\c{c}\~{a}o de tra\c{c}os de carbonato em solu\c{c}\~{a}o de hidr\'{o}xido de l\'{i}tio concentrado em sistema fechado." (\textbf{2019}).

403. Paruzzo, Federico Maria. \textit{New Approaches to NMR Crystallography}. No. THESIS. EPFL, \textbf{2019}.

404. Paruzzo, Federico M., and Lyndon Emsley. "High-resolution 1H NMR of powdered solids by homonuclear dipolar decoupling." \textit{Journal of Magnetic Resonance} 309 (\textbf{2019}): 106598.

405. Alzamil, Yasser. Optimising the quantitative analysis in functional pet brain imaging. Diss. Cardiff University, \textbf{2019}.

406. Walker, Patrick William, "War without oversight: Challenges to the development of autonomous weapons systems.", Thesis, University of Buckingham (\textbf{2019}).

407. Yang, Guofeng, et al. "Multiple Constrained Reweighted Penalized Least Squares for Spectral Baseline Correction." \textit{Applied Spectroscopy} (\textbf{2019}): 0003702819885002.

408. Zhang, Jing, Shuai Chen, and Guoxiang Sun. "Spectral and chromatographic overall analysis: An insight into chemical equivalence assessment of traditional Chinese medicine." \textit{Journal of Chromatography A} (\textbf{2019}): 460556.

409. Richter, Craig G., et al. "Brain rhythms shift and deploy attention." \textit{bioRxiv} (\textbf{2019}): 795567.

410. Chen, Weiqi, et al. "An automated microfluidic system for the investigation of asphaltene deposition and dissolution in porous media." \textit{Lab on a Chip} 19.21 (\textbf{2019}): 3628-3640.

411. Mukherjee, Soma, Soumi Betal, and Asoke Prasun Chattopadhyay. "Dual sensing and synchronous fluorescence spectroscopic monitoring of Cr3+ and Al3+ using a luminescent Schiff base: Extraction and DFT studies." \textit{Spectrochimica Acta Part A: Molecular and Biomolecular Spectroscopy} (\textbf{2019}): 117837.

412. Roy Daipayan, and Daniel W. Armstrong. "Fast super/subcritical fluid chromatographic enantioseparations on superficially porous particles bonded with broad selectivity chiral selectors relative to fully porous particles." \textit{Journal of Chromatography A} 1605 (\textbf{2019}): 360339.

413. Kang, Yuhao, and Azriel Z. Genack. "Time delay in a disordered topological system." \textit{arXiv preprint arXiv:1912.05151} (\textbf{2019}).

414. Chankvetadze, Bezhan. "Recent trends in preparation, investigation and application of polysaccharide-based chiral stationary phases for separation of enantiomers in high-performance liquid chromatography." \textit{TrAC Trends in Analytical Chemistry} (\textbf{2019}): 115709.

415. de Paula Pedroza, Ricardo Henrique. \textit{Development of methods based on NIR and Raman spectroscopies together with chemometric tools for the qualitative and quantitative analysis of gasoline}. MS thesis. The University of Bergen, \textbf{2019}.

416. Wolf, Moritz, et al. "Synthesis, characterisation and water\textendash{}gas shift activity of nano-particulate mixed-metal (Al, Ti) cobalt oxides." \textit{Dalton Transactions} 48.36 (\textbf{2019}): 13858-13868.

417. Welch, Christopher J. "High throughput analysis enables high throughput experimentation in pharmaceutical process research." \textit{Reaction Chemistry \& Engineering} 4.11 (\textbf{2019}): 1895-1911.

418. Mironov, N. A., et al. "Methods for Studying Petroleum Porphyrins." \textit{Petroleum Chemistry} 59.10 (\textbf{2019}): 1077-1091.

419. Yang, Guofeng, et al. "Spectral features extraction based on continuous wavelet transform and image segmentation for peak detection." \textit{Analytical Methods} (\textbf{2019}).

420. Briggs, Tokini Kiki. \textit{An Auto-Picking Algorithm for the Detection of Clay Seams in Potash Mines Using GPR Data}. Diss. Faculty of Graduate Studies and Research, University of Regina, \textbf{2019}.

421. Hong, Ning, et al. "High-Speed Rail Suspension System Health Monitoring Using Multi-Location Vibration Data." \textit{IEEE Transactions on Intelligent Transportation Systems} (\textbf{2019}).

422. Hu, Jennifer F., et al. "Sequencing-based quantitative mapping of the cellular small RNA landscape." \textit{bioRxiv} (\textbf{2019}): 841130.

423. Elsayad, Kareem. "Spectral Phasor Analysis for Brillouin Microspectroscopy." \textit{Frontiers in Physics} 7 (\textbf{2019}): 62.

424. Huang, Weinan, et al. "Morphology and cell wall composition changes in lignified cells from loquat fruit during postharvest storage." \textit{Postharvest Biology and Technology} 157 (\textbf{2019}): 110975.

425. Kupka, Teobald, et al. "Local aromaticity mapping in the vicinity of planar and nonplanar molecules." \textit{Magnetic Resonance in Chemistry} 57.7 (\textbf{2019}): 359-372.

426. Parigger, Christian G. "Measurements of Gaseous Hydrogen\textendash{}Nitrogen Laser-Plasma." \textit{Atoms} 7.3 (\textbf{2019}): 61.

427. Venara, J., et al. "Design and development of a portable ${\upbeta}$-spectrometer for 90Sr activity measurements in contaminated matrices." \textit{Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment} (\textbf{2019}).

428. Gallmeier, Esther A., et al. "Real time monitoring of the chemistry of hydroxylamine nitrate and iron as surrogates for nuclear materials processing." \textit{Separation Science and Technology} (\textbf{2019}): 1-9.

429. Hong, Ning, et al. "High-Speed Rail Suspension System Health Monitoring Using Multi-Location Vibration Data." \textit{IEEE Transactions on Intelligent Transportation Systems} (\textbf{2019}).

430. Kielar, Aneta, et al. "Slowing is slowing: Delayed neural responses to words are linked to abnormally slow resting state activity in primary progressive aphasia." \textit{Neuropsychologia} 129 (\textbf{2019}): 331-347.

431. Wu, Wenchang, et al. "Diffusivities in 1-Alcohols Containing Dissolved H2, He, N2, CO, or CO2 Close to Infinite Dilution." \textit{The Journal of Physical Chemistry B} 123.41 (\textbf{2019}): 8777-8790.

432. Park, Sungchan, K. A. N. G. Jooyoung, and Jungho Kim. "Ultrasound imaging apparatus and method for controlling the same." U.S. Patent Application 10/2 47,824, filed April 2, \textbf{2019}.

433. Renda, Fioranna, et al. "kSHREC 'Delta' reflects the shape of kinetochore rather than intrakinetochore tension." \textit{BioRxiv} (\textbf{2019}): 811075.

434. Santiago, Ruben, et al. "Methanol-Promoted Oxidation of Nitrogen Oxide (NO x) by Encapsulated Ionic Liquids." \textit{Environmental science \& technology} 53.20 (\textbf{2019}): 11969-11978.

435. Hu, Jennifer Fan. A systems-level view of the tRNA epitranscriptome: defining the role of tRNA abundance, stability, and modifications in the bacterial stress response. Diss. Massachusetts Institute of Technology, \textbf{2019}.

436. Weaver, Jordan S., Veronica Livescu, and Nathan A. Mara. "A comparison of adiabatic shear bands in wrought and additively manufactured 316L stainless steel using nano-indentation and electron backscatter diffraction." \textit{Journal of Materials Science} 55.4 (\textbf{2020}): 1738-1752.

437. Li, Dongmei, Zhiwei Zhu, and Da-Wen Sun. "Visualization of the in situ distribution of contents and hydrogen bonding states of cellular level water in apple tissues by confocal Raman microscopy." \textit{Analyst} (\textbf{2020}).

438. Tsai, Chong-Bin, Wei-Yu Hung, and Wei-Yen Hsu. "A Fast and Effective System for Analysis of Optokinetic Waveforms with a Low-Cost Eye Tracking Device." \textit{Healthcare}. Vol. 9. No. 1. Multidisciplinary Digital Publishing Institute, \textbf{2020}.

439. Elsayad, Kareem. "Spectral phasor analysis for Brillouin microspectroscopy." \textit{Frontiers in Physics} 7 (\textbf{2019}): 62.

440. Takis, Panteleimon G., et al. "SMolESY: An Efficient and Quantitative Alternative to On-Instrument Macromolecular 1 H-NMR Signal Suppression." \textit{Chemical Science} (\textbf{2020}).

441. Pipathanapoompron, Thalerngsak, et al. "Magnetic reader testing for asymmetric oscillation noise." \textit{Journal of Magnetism and Magnetic Materials} (\textbf{2020}): 167064.

442. Ito, Motohiro, et al. "Evaluation of cone-beam computed tomography over a small field of view in a water bath based on the modulation transfer function with repeating-edge oversampling." \textit{Journal of Oral Science} (\textbf{2020}): 20-0479.

443. Li, Tianjun, Long Chen, and Xiliang Lu. "An Alternating Direction Minimization based denoising method for extracted ion chromatogram." \textit{Chemometrics and Intelligent Laboratory Systems} 206 (\textbf{2020}): 104138.

444. Zhang, Jing, Shuai Chen, and Guoxiang Sun. "Spectral and chromatographic overall analysis: An insight into chemical equivalence assessment of traditional Chinese medicine." \textit{Journal of Chromatography A} 1610 (\textbf{2020}): 460556.

445. McPherson, David L., Richard Harris, and David Sorensen. "Functional Neuroimaging of the Central Auditory System." \textit{Advances in Audiology and Hearing Science: Volume 1: Clinical Protocols and Hearing Devices} (\textbf{2020}): 327.

446. Hebert, Michael J., and David H. Russell. "Tracking the Structural Evolution of 4-Aminobenzoic Acid in the Transition from Solution to the Gas Phase." \textit{The Journal of Physical Chemistry B} 124.11 (\textbf{2020}): 2081-2087.

447. Tang, Hui, et al. "On 2D-3D Image Feature Detections for Image-To-Geometry Registration in Virtual Dental Model." \textit{2020 IEEE International Conference on Visual Communications and Image Processing (VCIP)}. IEEE, \textbf{2020}.

448. Bhatia, Siddharth, and Karthikeyan Vasudevan. "Comparative proteomics of geographically distinct saw-scaled viper (Echis carinatus) venoms from India." \textit{Toxicon: X} 7 (\textbf{2020}): 100048.

449. Resentini, Alberto, et al. "Zircon as a provenance tracer: Coupling Raman spectroscopy and UPb geochronology in source-to-sink studies." \textit{Chemical Geology} 555 (\textbf{2020}): 119828.

450. Ajemigbitse, Moses A., Fred S. Cannon, and Nathaniel R. Warner. "A rapid method to determine 226Ra concentrations in Marcellus Shale produced waters using liquid scintillation counting." \textit{Journal of Environmental Radioactivity} 220 (\textbf{2020}): 106300.

451. Muirhead, D. K., et al. "Raman spectroscopy: an effective thermal marker in low temperature carbonaceous fold\textendash{}thrust belts." \textit{Geological Society, London, Special Publications} 490.1 (\textbf{2020}): 135-151.

452. Quilfen, Y., and B. Chapron. "On denoising satellite altimeter measurements for high-resolution geophysical signal analysis." \textit{Advances in Space Research} (\textbf{2020}).

453. Wu, Dan, Pol Mac Aonghusa, and Donal O'Shea. "Correlation of National and Healthcare Workers COVID-19 Infection Data; Implications for Large-scale Viral Testing Programs." \textit{medRxiv} (\textbf{2020}).

454. Battini, Davide, et al. "Modeling Approach and Finite Element Analyses of a Shape Memory Epoxy-Based Material." \textit{Conference of the Italian Association of Theoretical and Applied Mechanics}. Springer, Cham, \textbf{2019}.

455. Wu, Billy, et al. "An Energy Storage Device Monitoring Technique." U.S. Patent Application No. 16/088,016, \textbf{2020}.

456. Ge, X., et al. "Electrical and structural characterization of nano-carbon\textendash{}aluminum composites fabricated by electro-charging-assisted process." \textit{Carbon} 173: 115-125, \textbf{2021}.

456. Hsu, Gee-Sern Jison, et al. "A deep learning framework for heart rate estimation from facial videos." \textit{Neurocomputing} 417 (\textbf{2020}): 155-166.

457. Hammonds, James S., and Kimani A. Stancil. "Phonon effect based nanoscale temperature measurement." U.S. Patent No. 10,520,374. 31 Dec. \textbf{2019}.

458. Weaver, Jordan S., Veronica Livescu, and Nathan A. Mara. "A comparison of adiabatic shear bands in wrought and additively manufactured 316L stainless steel using nanoindentation and electron backscatter diffraction." \textit{Journal of Materials Science} 55.4 (\textbf{2020}): 1738-1752.

459. Gallagher, John Barry, Vishnu Prahalad, and John Aalders. "Inorganic and black carbon hotspots constrain blue carbon mitigation services across tropical seagrass and temperate tidal marshes." \textit{bioRxiv} (\textbf{2020}).

460. Wu, Wenchang, et al. "Mutual and Thermal Diffusivities as well as Fluid-Phase Equilibria of Mixtures of 1-Hexanol and Carbon Dioxide." \textit{The Journal of Physical Chemistry B} 124.12 (\textbf{2020}): 2482-2494.

461. Busa, William, Phillip H. Coelho, and Paul Getchel. "Lateral flow immunoassay test reader and method of use." U.S. Patent No. 10,823,746. 3 Nov. \textbf{2020}.

462. Dubrovkin, Joseph. \textit{Mathematical processing of spectral data in analytical chemistry: A guide to error analysis}. Cambridge Scholars Publishing, \textbf{2019}.

463. Bonnin-Pascual, Francisco, and Alberto Ortiz. "UWB-Based Self-Localization Strategies: A Novel ICP-Based Method and a Comparative Assessment for Noisy-Ranges-Prone Environments." \textit{Sensors} 20.19 (\textbf{2020}): 5613.

464. Chaumel, J\'{u}lia, et al. "Co-aligned chondrocytes: Zonal morphological variation and structured arrangement of cell lacunae in tessellated cartilage." \textit{Bone} (\textbf{2020}): 115264.

465. Bruendl, Stefan A., et al. "A New Emulation Platform for Real-time Machine Learning in Substance Use Data Streams." \textit{2020 IEEE 21st International Conference on Information Reuse and Integration for Data Science (IRI)}. IEEE, \textbf{2020}.

466. Cuyt, Annie, and Wen-shin Lee. "Parameter spectral analysis: scale and shift." \textit{arXiv preprint arXiv:2008.02125} (\textbf{2020}).

467. Li, Wenda, et al. "A novel processing methodology for traffic-speed road surveys using point lasers." \textit{IEEE Transactions on Intelligent Transportation Systems} (\textbf{2019}).

468. Li, Yuanlu, Kun Li, and Qiyu Lu. "Applying segmentation and classification to improve performance of smoothing." \textit{Digital Signal Processing} 109: 102913, \textbf{2021}.

469. Rutt, Daryl, et al. "Importance of Accurate and Detailed Data Processing of Laser Mapping in Coke Drum." \textit{Pressure Vessels and Piping Conference}. Vol. 58943. American Society of Mechanical Engineers, \textbf{2019}.

470. Al-Mbaideen, Amneh A. "Application of moving average filter for the quantitative analysis of the NIR spectra." \textit{Journal of Analytical Chemistry} 74.7 (\textbf{2019}): 686-692.

471. Vitali, L., et al. "Infrared image processing for local convective heat transfer measurements in rib-enhanced channels." \textit{Journal of Physics: Conference Series}. Vol. 1599. No. 1. IOP Publishing, \textbf{2020}.

472. Vergel, \'{A}ngelo Joseph Soto, Luis Enrique Mendoza, and Byron Medina Delgado. "Analysis of energy and major components in chromatographic signals for the diagnosis of prostate cancer." \textit{Respuestas} 24.1 (\textbf{2019}): 76-85.

473. Zhang, Genwei, et al. "Multiscale orthogonal matching pursuit algorithm combined with peak model for interpreting ion mobility spectra and achieving quantitative analysis." \textit{Analytica Chimica Acta} (\textbf{2020}).

474. Zhang, Lei, et al. "WiDIGR: Direction-Independent Gait Recognition System Using Commercial Wi-Fi Devices." \textit{IEEE Internet of Things Journal} 7.2 (\textbf{2019}): 1178-1191.

475. Wiegand, Patrick. "Raman signal position correction using relative integration parameters." U.S. Patent No. 10,627,289. 21 Apr. \textbf{2020}.

476. Botezatu, Irina V., et al. "Asymmetric mutant-enriched polymerase chain reaction and quantitative DNA melting analysis of KRAS mutation in colorectal cancer." \textit{Analytical Biochemistry} 590 (\textbf{2020}): 113517.

477. Joubaud, Thomas, and Gr\'{e}gory Pallone. "Electroacoustic method for the calibration of a heterogeneous distributed speaker system." \textbf{\textit{2020}} \textit{28th European Signal Processing Conference (EUSIPCO)}. IEEE.

478. Xiang, YuChen, et al. "Background-free fibre optic Brillouin probe for remote mapping of micromechanics." \textit{arXiv preprint arXiv:2005.12266} (\textbf{2020}).

479. Huang, Ronggang, et al. "Optical frequency and phase information-based fusion approach for image rotation symmetry detection." \textit{Optics Express} 28.13 (\textbf{2020}): 18577-18595.

480. Sosin, M., et al. "Impact of vibrations and reflector movements on the measurement uncertainty of Fourier-based frequency sweeping interferometry." \textit{Photonic Instrumentation Engineering VII}. Vol. 11287. International Society for Optics and Photonics, \textbf{2020}.

481. Chakraborty, Saikat, and Anup Nandy. "Automatic Diagnosis of Cerebral Palsy Gait Using Computational Intelligence Techniques: A Low-Cost Multi-Sensor Approach." \textit{IEEE Transactions on Neural Systems and Rehabilitation Engineering} 28.11 (\textbf{2020}): 2488-2496.

482. Kim, Najin, et al. "Hygroscopicity of urban aerosols and its link to size-resolved chemical composition during spring and summer in Seoul, Korea." \textit{Atmospheric Chemistry and Physics} 20.19 (\textbf{2020}): 11245-11262.

483. Ma, Te, et al. "Rapid and nondestructive evaluation of hygroscopic behavior changes of thermally modified softwood and hardwood samples using near-infrared hyperspectral imaging (NIR-HSI)." \textit{Holzforschung} 1.ahead-of-print (\textbf{2020}).

484. Laskaris, Nick, et al. "EVIDENCE OF AU-HG GILDING PROCESS IN POST BYZANTINE ECCLESIASTICAL SILVERWARES (CHALICES) OF EASTERN THESSALY BY PXRF." \textit{Mediterranean Archaeology \& Archaeometry} 13.1 (\textbf{2020}).

485. Obaydo, Reem H., and Amir Alhaj Sakur. "Spectrophotometric strategies for the analysis of binary combinations with minor component based on isoabsorptive point's leveling effect: An application on ciprofloxacin and fluocinolone acetonide in their recently delivered co-formulation." \textit{Spectrochimica Acta Part A: Molecular and Biomolecular Spectroscopy} 219 (\textbf{2019}): 186-194.

486. Ma, Liya, and Peter Schegner. "State duration based event detection for domestic power disaggregation." \textit{2019 IEEE Milan PowerTech}. IEEE, \textbf{2019}.

497.\begin{otherlanguage*}{russian}Коломиец, O. O., and C. В. Глушен. "Суточный ритм роста листьев и пролиферации клеток у перца стручкового (Capsicum annuum L.)." \textit{Известия Национальной академии наук Беларуси. Серия биологических наук} 
\end{otherlanguage*} 64.4 (\textbf{2019}): 448-455.

498. Reynes, Julien, Pierre Lanari, and J\"{o}rg Hermann. "A mapping approach for the investigation of Ti\textendash{}OH relationships in metamorphic garnet." \textit{Contributions to Mineralogy and Petrology} 175 (\textbf{2020}): 1-17.

499. Shumeyko, Christopher M., et al. "Tunable mechanical behavior of graphene nanoribbon-metal composites fabricated through an electrocharge-assisted process." \textit{Materials Science and Engineering: A} 800 (\textbf{2020}): 140289.

500. Psyrras, N., et al. "Physical Modeling of the Seismic Response of Gas Pipelines in Laterally Inhomogeneous Soil." \textit{Journal of Geotechnical and Geoenvironmental Engineering} 146.5 (\textbf{2020}): 04020031.

501. Chen, Hong-Jia, et al. "Self-potential ambient noise and spectral relationship with urbanization, seismicity, and strain rate revealed via the Taiwan Geoelectric Monitoring Network." \textit{Journal of Geophysical Research: Solid Earth} 125.1 (\textbf{2020}): e2019JB018196.

502. Mustafa, M. A., et al. "Amplification and structure of streamwise-velocity fluctuations in compression-corner shock-wave/turbulent boundary-layer interactions." \textit{Journal of Fluid Mechanics} 863 (\textbf{2019}): 1091-1122.

503. Mekonnen, Alemu, et al. "Improved Biomass Cookstove Use in the Longer Run: Results from a Field Experiment in Rural Ethiopia." \textit{World Bank Policy Research Working Paper} 9272 (\textbf{2020).}

504. Bradshaw, Peter R., et al. "Kinetic modelling of acyl glucuronide and glucoside reactivity and development of structure\textendash{}property relationships." \textit{Organic \& Biomolecular Chemistry} 18.7 (\textbf{2020}): 1389-1401.

505. Bluffstone, Randall, et al. "Does providing improved biomass cooking stoves free-of-charge reduce regular usage? Do use incentives promote habits?." \textit{LAND ECONOMICS} (\textbf{2020}).

506. Guo, Qimei, et al. "Mediterranean Outflow Water dynamics across the middle Pleistocene transition based on a 1.3 million-year benthic foraminiferal record off the Portuguese margin." \textit{Quaternary Science Reviews} 247 (\textbf{2020}): 106567.

507. Mustafa, Muhammad A., David Shekhtman, and Nick J. Parziale. "Single-Laser Krypton Tagging Velocimetry (KTV) Investigation of Air and N2 Boundary-Layer Flows Over a Hollow Cylinder in the Stevens Shock Tube." \textit{AIAA Scitech 2019 Forum}. \textbf{2019}.

508. Wang, M., et al. "Evolution of dislocation and twin densities in a Mg alloy at quasi-static and high strain rates." \textit{Acta Materialia} 201 (\textbf{2020}): 102-113.

509. AlOmar, AbdulAzeez S. "Accurate Chebyshev Approximations for the Width of the Voigt Profile, Differential Peaks, and Deconvolution of the Lorentzian Width." \textit{Optik} 225: 165533, \textbf{2021}.

510. Hoyer, Jorgen, et al. "Mapping calcium dynamics in a developing tubular structure." \textit{bioRxiv} (\textbf{2020}).

511. Hansen, Lars N., et al. "Low-Temperature Plasticity in Olivine: Grain Size, Strain Hardening, and the Strength of the Lithosphere." \textit{Journal of Geophysical Research. Solid Earth} 124.6 (\textbf{2019}).

512. Du, Siqi, et al. "Complete identification of all 20 relevant epimeric peptides in ${\upbeta}$-amyloid: a new HPLC-MS based analytical strategy for Alzheimer's research." \textit{Chemical Communications} 56.10 (\textbf{2020}): 1537-1540.

513. Hebden, Jeremy C. "Exploring the feasibility of wavelength modulated near-infrared spectroscopy." \textit{Journal of Biomedical Optics} 25.11 (\textbf{2020}): 110501.

514. Aikin, Timothy J., et al. "MAPK activity dynamics regulate non-cell autonomous effects of oncogene expression." \textit{Elife} 9 (\textbf{2020}): e60541.

515. Pepermans, Vincent, et al. "Column-in-Valve Designs to Minimize Extra-Column Volumes." \textit{Journal of Chromatography A} (\textbf{2020}): 461779.
